---
title: "Methods-K45"
author: "Evan Odell"
date: "03/09/2018"
output: html_document
---


```{r STM-classification-prep, eval=FALSE, include=FALSE}
library(stm)
library(quanteda)
library(quanteda.corpora)
library(readr)


library(stm)
library(quanteda)
library(quanteda.corpora)
library(readr)

lab_corpus <- read_rds("data/lab_corpus.rds")

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister", "c")

lab_corpus_stm <- dfm(lab_corpus, remove_punct = TRUE,
                          remove = parliament_stopwords, verbose = TRUE) %>%
  convert(to = "stm", docvars = NULL)

lab_corpus_stm$meta$short_list <- as.factor(lab_corpus_stm$meta$short_list)

write_rds(lab_corpus_stm, "data/lab_corpus_stm.rds")

```


```{r stm-analysis-k45, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.cap="\\label{k45-network}Fruchterman-Reingold plot of k45 Network"}
library(readr)
library(stm)
library(viridis)
library(dplyr)
library(igraph)
library(ggplot2)
library(quanteda)
#library(tidystm)

corr_topic_k45 <- read_rds("data/corr_topic_k45_m.rds")

prep_k45 <- read_rds("data/prep_k45_m.rds")

lab_corpus_stm <- read_rds("data/lab_corpus_stm.rds")

topic_model_k45 <- read_rds("data/topic_model_k45_m.rds")

prep_df_k45 <- summary(prep_k45)[[3]]

prep_df_k45 <- as.data.frame(do.call(rbind, prep_df_k45))

prep_df_k45$topic <- NA

prep_df_k45$topic <- rep(1:45, each = 2)

prep_df_k45$type <- row.names(prep_df_k45)

prep_df_k45$type <- gsub("\\.[0-9][0-9]", "", prep_df_k45$type)

prep_df_k45$type <- gsub("\\.[0-9]", "", prep_df_k45$type)

prep_df_k45$type <- gsub("\\.$", "", prep_df_k45$type)

prep_df_k45_coeff <- prep_df_k45 %>% filter(type == "short_listTRUE")

vlabels=NULL
layout=NULL

topics <- 1:nrow(corr_topic_k45$posadj)
  
x <- corr_topic_k45$posadj[topics, topics]
  
g <- igraph::graph.adjacency(x, mode="directed", weighted=TRUE, diag=FALSE)
igraph::E(g)$size <- 1
igraph::E(g)$lty <- 2
igraph::E(g)$color <- "black"
igraph::V(g)$label <- topics

plotcord_k45 <- data.frame(layout_with_fr(g))
  
edgelist_k45 <- get.edgelist(g)

#convert to a four column edge data frame with source and destination coordinates
edges_k45 <- data.frame(plotcord_k45[edgelist_k45[,1],], 
                    plotcord_k45[edgelist_k45[,2],])
colnames(edges_k45) <- c("X1","Y1","X2","Y2")

plotcord_k45$topic <- as.numeric(row.names(plotcord_k45))
  
plotcord_k45 <- plotcord_k45 %>% left_join(prep_df_k45_coeff)

lab_corpus_fem_stm$meta$eo_id <- docnames(lab_corpus_fem_stm$documents)

topic_dt_k45 <- make.dt(topic_model_k45, lab_corpus_fem_stm$meta)

topic_dt_k45$assigned_topic <- colnames(topic_dt_k45[,2:46])[max.col(topic_dt_k45[,2:46],ties.method="random")]

topic_dt_k45$assigned_topic <- as.factor(topic_dt_k45$assigned_topic)

## Reordering x$assigned_topic
topic_dt_k45$assigned_topic <- factor(topic_dt_k45$assigned_topic, 
                           levels=c("Topic1", "Topic2", "Topic3",
                                    "Topic4", "Topic5", "Topic6",
                                    "Topic7", "Topic8", "Topic9",
                                    "Topic10", "Topic11", "Topic12",
                                    "Topic13", "Topic14", "Topic15",
                                    "Topic16", "Topic17", "Topic18",
                                    "Topic19", "Topic20", "Topic21",
                                    "Topic22", "Topic23", "Topic24",
                                    "Topic25", "Topic26", "Topic27",
                                    "Topic28", "Topic29", "Topic30",
                                    "Topic31", "Topic32", "Topic33",
                                    "Topic34", "Topic35", "Topic36",
                                    "Topic37", "Topic38", "Topic39",
                                    "Topic40", "Topic41", "Topic42",
                                    "Topic43", "Topic44", "Topic45"))

topic_dt_k45_2 <- topic_dt_k45 %>% 
  group_by(assigned_topic)  %>% 
  summarise(count = n(),
            mean_word_count = mean(word_count)) %>%
  mutate(freq = count/sum(count))

plotcord_k45$assigned_topic <- paste0("Topic", plotcord_k45$topic)

plotcord_k45 <- plotcord_k45 %>% left_join(topic_dt_k45_2)

p_network_k45 <- ggplot() + 
  geom_segment(aes(x=X1, y=Y1, xend = X2, yend = Y2),
               data=edges_k45, size = 0.5, colour="grey") +
  geom_point(data = plotcord_k45, aes(X1, X2, colour = Estimate, size = freq)) + 
  geom_text(aes(X1, X2, label=topic), hjust="center", vjust="top",
            size = 5, data = plotcord_k45) + 
  scale_colour_viridis(breaks = c(max(plotcord_k45$Estimate),
                                  min(plotcord_k45$Estimate)), 
                       labels = c("More AWS", "More non-AWS"),
                       name=NULL, option = "plasma",
                       end = 0.85, begin = 0.15) + 
  scale_size(guide = "none") + 
  theme_void() + 
  theme(legend.position = "bottom",
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),  
    axis.title.x = element_blank(), 
    axis.title.y = element_blank())

ggsave("p_network_k45.svg", plot = p_network_k45, path="plots", 
       device = "svg", width = 20, height = 20, units = "cm")

p_network_k45
```


The `stm` package includes the `estimateEffect` function to create a regression model (Table \ref{estimate-table-k45}) using individual documents (speeches) as individual observations, with the number of documents fitting each topic as the dependent variable and model covariates (AWS status) as independent variables. 

```{r estimate-table-k45, echo=FALSE, fig.cap="\\label{estimate-table-k45}"}
library(knitr)
library(kableExtra)
library(dplyr)

row.names(prep_df_k45) <- NULL
prep_df_k45$type <- gsub("X.Intercept", "Intercept", prep_df_k45$type)
prep_df_k45$type <- gsub("short_listTRUE", "Shortlist", prep_df_k45$type)


prep_df_k45 <- prep_df_k45 %>% rename(
  "p" = "Pr(>|t|)"
)

prep_df_k45$stars <- case_when(prep_df_k45$p < 0.001 ~ "***", 
                               prep_df_k45$p < 0.01 ~ "**",
                               prep_df_k45$p < 0.05 ~ "*", 
                               TRUE ~ "")

prep_df_k45_2 <- prep_df_k45 %>% select(type, Estimate,
                                        `Std. Error`, `t value`, p, stars) %>%
  mutate(p = pixiedust::pval_string(p,  digits = 4))

kable(prep_df_k45_2,  booktabs = TRUE, longtable = TRUE, 
      caption = "Estimate Effects -- k45",
      col.names = c("", "Estimate", "Standard Error",
                    "t value", "Pr(>|t|)", ""),
      align = c("l","r","r","r","r", "l")) %>%
    kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE ) %>%
  group_rows(index = c("Topic 1 -- Business" = 2,
                        "Topic 2 -- Roads" = 2,
                        "Topic 3 -- Members" = 2,
                        "Topic 4 -- Gender" = 2,
                        "Topic 5 -- Housing" = 2,
                        "Topic 6 -- Questions" = 2,
                        "Topic 7 -- Technology" = 2,
                        "Topic 8 -- Food & farming" = 2,
                        "Topic 9 -- Animals" = 2,
                        "Topic 10 -- Disease" = 2,
                        "Topic 11 -- Parties" = 2,
                        "Topic 12 -- Health Care" = 2,
                        "Topic 13 -- Disasters" = 2,
                        "Topic 14 -- Energy" = 2,
                        "Topic 15 -- Volunteering" = 2,
                        "Topic 16 -- Infrastructure" = 2,
                        "Topic 17 -- Local authorities" = 2,
                        "Topic 18 -- Universities & skills" = 2,
                        "Topic 19 -- Schools" = 2,
                        "Topic 20 -- Transport" = 2,
                        "Topic 21 -- Police" = 2,
                        "Topic 22 -- Budgets & tax" = 2,
                        "Topic 23 -- Drugs" = 2,
                        "Topic 24 -- Culture & sport" = 2,
                        "Topic 25 -- Children & familiesies" = 2,
                        "Topic 26 -- Planning & land-use" = 2,
                        "Topic 27 -- Security" = 2,
                        "Topic 28 -- Elections" = 2,
                        "Topic 29 -- Benefits & pensions" = 2,
                        "Topic 30 -- Call to action" = 2,
                        "Topic 31 -- Reports" = 2,
                        "Topic 32 -- Disability" = 2,
                        "Topic 33 -- Amendments" = 2,
                        "Topic 34 -- Justice" = 2,
                        "Topic 35 -- Military intervention" = 2,
                        "Topic 36 -- Financial system" = 2,
                        "Topic 37 -- Debate" = 2,
                        "Topic 38 -- Public bodies" = 2,
                        "Topic 39 -- Devolution" = 2,
                        "Topic 40 -- Bills" = 2,
                        "Topic 41 -- European Union" = 2,
                        "Topic 42 -- Environment" = 2,
                        "Topic 43 -- Constituency" = 2,
                        "Topic 44 -- Responses" = 2,
                        "Topic 45 -- Interventions" = 2))
```


```{r estimate-table-subsets-k45, include=FALSE}
prep_df_k45_sig_check <- prep_df_k45 %>% 
   mutate(topic = recode(topic,
                         "1" = "Business",
                         "2" = "Roads",
                         "3" = "Members",
                         "4" = "Gender",
                         "5" = "Housing",
                        "6" = "Questions",
                        "7" = "Technology",
                        "8" = "Food & farming",
                        "9" = "Animals",
                        "10" = "Disease",
                        "11" = "Parties",
                        "12" = "Health Care",
                        "13" = "Disasters",
                        "14" = "Energy",
                        "15" = "Volunteering",
                        "16" = "Infrastructure",
                        "17" = "Local authorities",
                        "18" = "Universities & skills",
                        "19" = "Schools",
                        "20" = "Transport",
                        "21" = "Police",
                        "22" = "Budgets & tax",
                        "23" = "Drugs",
                        "24" = "Culture & sport",
                        "25" = "Children & familiesies",
                        "26" = "Planning & land-use",
                        "27" = "Security",
                        "28" = "Elections",
                        "29" = "Benefits & pensions",
                        "30" = "Call to action",
                        "31" = "Reports",
                        "32" = "Disability",
                        "33" = "Amendments",
                        "34" = "Justice",
                        "35" = "Military intervention",
                        "36" = "Financial system",
                        "37" = "Debate",
                        "38" = "Public bodies",
                        "39" = "Devolution",
                        "40" = "Bills",
                        "41" = "European Union",
                        "42" = "Environment",
                        "43" = "Constituency",
                        "44" = "Responses",
                        "45" = "Interventions"))

prep_df_k45_no_sig <- prep_df_k45_sig_check %>%
  filter(type == "Shortlist" & p >= 0.05)

prep_df_k45_sig_1_5 <- prep_df_k45_sig_check %>%
  filter(type == "Shortlist" & p < 0.05 & p >= 0.001)

```


In all but `r nrow(prep_df_k45_no_sig)` topics (`r prep_df_k45_no_sig$topic`) the model found _p_ values of < 0.05, and in every topic except the aforemention and `r prep_df_k45_sig_1_5$topic`, _p_ values of < 0.001.


```{r stm-excl-coh-k45, echo=FALSE, fig.cap="\\label{k45-coherence}Coherence of k45 Topic Models"}

library(ggrepel)

sem_test_k45 <- semanticCoherence(topic_model_k45, lab_corpus_fem_stm$documents)

exc_test_k45 <- exclusivity(topic_model_k45)

sem_exc_k45 <- tibble::tibble(topic = 1:45, sem_test_k45, exc_test_k45)

p_sem_exc_k45 <- ggplot(sem_exc_k45, aes(y=exc_test_k45, x = sem_test_k45)) + 
  geom_point() + 
  geom_label_repel(aes(label = topic)) +
  #coord_cartesian(xlim = c(-200,0), ylim = c(9.4, 10)) + 
  labs(x="Semantic Coherence", y = "Exclusivity")

ggsave("p_sem_exc_k45.svg", plot = p_sem_exc_k45, path="plots", 
       device = "svg", width = 20, height = 20, units = "cm")

p_sem_exc_k45
```



```{r topic-diversity-k45, echo=FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
#head(topic_dt_k30)

#summary(topic_dt_k30$mnis_id)

topic_dt_k45_div <- topic_dt_k45 %>% 
  mutate(assigned_topic = gsub("Topic", "Topic ", assigned_topic)) %>% 
  group_by(assigned_topic, mnis_id) %>%
  tally() %>% ungroup() %>% 
  group_by(assigned_topic)  %>%
  summarise(distinct_n5 = sum(n >= 5),
            distinct = n()) %>%
  ungroup() %>%
  select(assigned_topic, distinct, distinct_n5) %>%
   mutate(assigned_topic = factor(assigned_topic,
                                  levels=c("Topic 1", "Topic 2", "Topic 3",
                                    "Topic 4", "Topic 5", "Topic 6",
                                    "Topic 7", "Topic 8", "Topic 9",
                                    "Topic 10", "Topic 11", "Topic 12",
                                    "Topic 13", "Topic 14", "Topic 15",
                                    "Topic 16", "Topic 17", "Topic 18",
                                    "Topic 19", "Topic 20", "Topic 21",
                                    "Topic 22", "Topic 23", "Topic 24",
                                    "Topic 25", "Topic 26", "Topic 27",
                                    "Topic 28", "Topic 29", "Topic 30",
                                    "Topic 31", "Topic 32", "Topic 33",
                                    "Topic 34", "Topic 35", "Topic 36",
                                    "Topic 37", "Topic 38", "Topic 39",
                                    "Topic 40", "Topic 41", "Topic 42",
                                    "Topic 43", "Topic 44", "Topic 45")),
     assigned_topic = recode(assigned_topic,
                                  "Topic 1" = "Business (Topic 1)",
                                  "Topic 2" = "Roads (Topic 2)",
                                  "Topic 3" = "Members (Topic 3)",
                                  "Topic 4" = "Gender (Topic 4)",
                                  "Topic 5" = "Housing (Topic 5)",
                                  "Topic 6" = "Questions (Topic 6)",
                                  "Topic 7" = "Technology (Topic 7)",
                                  "Topic 8" = "Food & farming (Topic 8)",
                                  "Topic 9" = "Animals (Topic 9)",
                                  "Topic 10" = "Disease (Topic 10)",
                                  "Topic 11" = "Parties (Topic 11)",
                                  "Topic 12" = "Health Care (Topic 12)",
                                  "Topic 13" = "Disasters (Topic 13)",
                                  "Topic 14" = "Energy (Topic 14)",
                                  "Topic 15" = "Volunteering (Topic 15)",
                                  "Topic 16" = "Infrastructure (Topic 16)",
                                  "Topic 17" = "Local authorities (Topic 17)",
                                  "Topic 18" = "Universities & skills (Topic 18)",
                                  "Topic 19" = "Schools (Topic 19)",
                                  "Topic 20" = "Transport (Topic 20)",
                                  "Topic 21" = "Police (Topic 21)",
                                  "Topic 22" = "Budgets & tax (Topic 22)",
                                  "Topic 23" = "Drugs (Topic 23)",
                                  "Topic 24" = "Culture & sport (Topic 24)",
                                  "Topic 25" = "Children & families (Topic 25)",
                                  "Topic 26" = "Planning & land-use (Topic 26)",
                                  "Topic 27" = "Security (Topic 27)",
                                  "Topic 28" = "Elections (Topic 28)",
                                  "Topic 29" = "Benefits & pensions (Topic 29)",
                                  "Topic 30" = "Call to action (Topic 30)",
                                  "Topic 31" = "Reports (Topic 31)",
                                  "Topic 32" = "Disability (Topic 32)",
                                  "Topic 33" = "Amendments (Topic 33)",
                                  "Topic 34" = "Justice (Topic 34)",
                                  "Topic 35" = "Military intervention (Topic 35)",
                                  "Topic 36" = "Financial system (Topic 36)",
                                  "Topic 37" = "Debate (Topic 37)",
                                  "Topic 38" = "Public bodies (Topic 38)",
                                  "Topic 39" = "Devolution (Topic 39)",
                                  "Topic 40" = "Bills (Topic 40)",
                                  "Topic 41" = "European Union (Topic 41)",
                                  "Topic 42" = "Environment (Topic 42)",
                                  "Topic 43" = "Constituency (Topic 43)",
                                  "Topic 44" = "Responses (Topic 44)",
                                  "Topic 45" = "Interventions (Topic 45)")) %>%
  arrange(assigned_topic)

kable(topic_dt_k45_div,  booktabs = TRUE, longtable = TRUE, 
      caption = "Distribution of Topics Among Female Labour MPs -- K45",
      col.names = c("Topic", "One or more speeches", "Five or more speeches"),
      align = c("l","r","r")) %>%
    kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE )

topic_dt_k45_div$prop <- topic_dt_k45_div$distinct_n5/topic_dt_k45_div$distinct
```


```{r topic-dt3-creation-k45, include=FALSE}
topic_dt_k45_3 <- topic_dt_k45 %>%
  group_by(assigned_topic, short_list) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  spread(key = "short_list", value = "count") %>%
  rename("AWS" = "TRUE", "non_AWS" = "FALSE") %>%
  mutate(AWS_freq = AWS/sum(AWS, na.rm = TRUE),
         non_AWS_freq = non_AWS/sum(non_AWS, na.rm = TRUE),
         assigned_topic = gsub("Topic", "Topic ", assigned_topic)) %>%
  select(assigned_topic, AWS, AWS_freq, non_AWS, non_AWS_freq) %>%
  left_join(topic_man_dt_k45_2)


topic_dt_k45_4 <- topic_dt_k45_3 %>% 
    mutate(AWS_freq = paste0(round((AWS_freq*100), 2), "%"),
          non_AWS_freq = paste0(round((non_AWS_freq*100), 2), "%"),
          AWS = formatC(AWS, big.mark = ","),
          non_AWS = formatC(non_AWS, big.mark = ","),
          man_freq = paste0(round((man_freq*100), 2), "%"),
          man_count = formatC(man_count, big.mark = ","),
     assigned_topic = recode(assigned_topic,
                                  "Topic 1" = "Business (Topic 1)",
                                  "Topic 2" = "Roads (Topic 2)",
                                  "Topic 3" = "Members (Topic 3)",
                                  "Topic 4" = "Gender (Topic 4)",
                                  "Topic 5" = "Housing (Topic 5)",
                                  "Topic 6" = "Questions (Topic 6)",
                                  "Topic 7" = "Technology (Topic 7)",
                                  "Topic 8" = "Food & farming (Topic 8)",
                                  "Topic 9" = "Animals (Topic 9)",
                                  "Topic 10" = "Disease (Topic 10)",
                                  "Topic 11" = "Parties (Topic 11)",
                                  "Topic 12" = "Health Care (Topic 12)",
                                  "Topic 13" = "Disasters (Topic 13)",
                                  "Topic 14" = "Energy (Topic 14)",
                                  "Topic 15" = "Volunteering (Topic 15)",
                                  "Topic 16" = "Infrastructure (Topic 16)",
                                  "Topic 17" = "Local authorities (Topic 17)",
                                  "Topic 18" = "Universities & skills (Topic 18)",
                                  "Topic 19" = "Schools (Topic 19)",
                                  "Topic 20" = "Transport (Topic 20)",
                                  "Topic 21" = "Police (Topic 21)",
                                  "Topic 22" = "Budgets & tax (Topic 22)",
                                  "Topic 23" = "Drugs (Topic 23)",
                                  "Topic 24" = "Culture & sport (Topic 24)",
                                  "Topic 25" = "Children & families (Topic 25)",
                                  "Topic 26" = "Planning & land-use (Topic 26)",
                                  "Topic 27" = "Security (Topic 27)",
                                  "Topic 28" = "Elections (Topic 28)",
                                  "Topic 29" = "Benefits & pensions (Topic 29)",
                                  "Topic 30" = "Call to action (Topic 30)",
                                  "Topic 31" = "Reports (Topic 31)",
                                  "Topic 32" = "Disability (Topic 32)",
                                  "Topic 33" = "Amendments (Topic 33)",
                                  "Topic 34" = "Justice (Topic 34)",
                                  "Topic 35" = "Military intervention (Topic 35)",
                                  "Topic 36" = "Financial system (Topic 36)",
                                  "Topic 37" = "Debate (Topic 37)",
                                  "Topic 38" = "Public bodies (Topic 38)",
                                  "Topic 39" = "Devolution (Topic 39)",
                                  "Topic 40" = "Bills (Topic 40)",
                                  "Topic 41" = "European Union (Topic 41)",
                                  "Topic 42" = "Environment (Topic 42)",
                                  "Topic 43" = "Constituency (Topic 43)",
                                  "Topic 44" = "Responses (Topic 44)",
                                  "Topic 45" = "Interventions (Topic 45)"))

```

```{r topic-summary-table-k45, echo=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)

kable(topic_dt_k45_4,  booktabs = TRUE, longtable = TRUE, 
      caption = "Count and Distribution of Topics -- k45",
      col.names = c("Topic Number", "AWS Speeches", "Percent of AWS Speeches",
                    "Non-AWS Speeches", "Percent of non-AWS Speeches",
                    "Male MP Speeches", "Percent of Male MP Speeches"),
      align = c("l","r","r","r","r","r","r")) %>%
    kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE )
```


```{r k45-topic-pyramid, echo=FALSE, fig.height=9, fig.cap="\\label{k45-topic-pyramid-plot}k45 Pyramid Chart"}

topic_dt_k45_5 <- topic_dt_k45_3 %>% 
  select(-man_count, -man_freq, -non_AWS, -AWS) %>%
  gather("aws_status", "perc", -assigned_topic) %>%
   mutate(assigned_topic = factor(assigned_topic,
                                   levels=c("Topic 1", "Topic 2", "Topic 3",
                                    "Topic 4", "Topic 5", "Topic 6",
                                    "Topic 7", "Topic 8", "Topic 9",
                                    "Topic 10", "Topic 11", "Topic 12",
                                    "Topic 13", "Topic 14", "Topic 15",
                                    "Topic 16", "Topic 17", "Topic 18",
                                    "Topic 19", "Topic 20", "Topic 21",
                                    "Topic 22", "Topic 23", "Topic 24",
                                    "Topic 25", "Topic 26", "Topic 27",
                                    "Topic 28", "Topic 29", "Topic 30",
                                    "Topic 31", "Topic 32", "Topic 33",
                                    "Topic 34", "Topic 35", "Topic 36",
                                    "Topic 37", "Topic 38", "Topic 39",
                                    "Topic 40", "Topic 41", "Topic 42",
                                    "Topic 43", "Topic 44", "Topic 45")),
           assigned_topic = recode(assigned_topic,
                                  "Topic 1" = "Business (Topic 1)",
                                  "Topic 2" = "Roads (Topic 2)",
                                  "Topic 3" = "Members (Topic 3)",
                                  "Topic 4" = "Gender (Topic 4)",
                                  "Topic 5" = "Housing (Topic 5)",
                                  "Topic 6" = "Questions (Topic 6)",
                                  "Topic 7" = "Technology (Topic 7)",
                                  "Topic 8" = "Food & farming (Topic 8)",
                                  "Topic 9" = "Animals (Topic 9)",
                                  "Topic 10" = "Disease (Topic 10)",
                                  "Topic 11" = "Parties (Topic 11)",
                                  "Topic 12" = "Health Care (Topic 12)",
                                  "Topic 13" = "Disasters (Topic 13)",
                                  "Topic 14" = "Energy (Topic 14)",
                                  "Topic 15" = "Volunteering (Topic 15)",
                                  "Topic 16" = "Infrastructure (Topic 16)",
                                  "Topic 17" = "Local authorities (Topic 17)",
                                  "Topic 18" = "Universities & skills (Topic 18)",
                                  "Topic 19" = "Schools (Topic 19)",
                                  "Topic 20" = "Transport (Topic 20)",
                                  "Topic 21" = "Police (Topic 21)",
                                  "Topic 22" = "Budgets & tax (Topic 22)",
                                  "Topic 23" = "Drugs (Topic 23)",
                                  "Topic 24" = "Culture & sport (Topic 24)",
                                  "Topic 25" = "Children & families (Topic 25)",
                                  "Topic 26" = "Planning & land-use (Topic 26)",
                                  "Topic 27" = "Security (Topic 27)",
                                  "Topic 28" = "Elections (Topic 28)",
                                  "Topic 29" = "Benefits & pensions (Topic 29)",
                                  "Topic 30" = "Call to action (Topic 30)",
                                  "Topic 31" = "Reports (Topic 31)",
                                  "Topic 32" = "Disability (Topic 32)",
                                  "Topic 33" = "Amendments (Topic 33)",
                                  "Topic 34" = "Justice (Topic 34)",
                                  "Topic 35" = "Military intervention (Topic 35)",
                                  "Topic 36" = "Financial system (Topic 36)",
                                  "Topic 37" = "Debate (Topic 37)",
                                  "Topic 38" = "Public bodies (Topic 38)",
                                  "Topic 39" = "Devolution (Topic 39)",
                                  "Topic 40" = "Bills (Topic 40)",
                                  "Topic 41" = "European Union (Topic 41)",
                                  "Topic 42" = "Environment (Topic 42)",
                                  "Topic 43" = "Constituency (Topic 43)",
                                  "Topic 44" = "Responses (Topic 44)",
                                  "Topic 45" = "Interventions (Topic 45)"))#,

topic_dt_k45_5$perc[is.na(topic_dt_k45_5$perc)] <- 0

p_k45_pyramid <- ggplot(data = topic_dt_k45_5, 
                        aes(x = assigned_topic, y = perc, fill = aws_status)) +
  geom_bar(data = filter(topic_dt_k45_5, aws_status == "non_AWS_freq"),
           stat = "identity" ) + 
  geom_bar(data = filter(topic_dt_k45_5, aws_status == "AWS_freq"),
           stat = "identity", aes(y = -perc) ) + 
  geom_bar(data = filter(topic_dt_k45_5, aws_status == "AWS_freq"),
           stat = "identity", aes(color = aws_status),
           alpha = 0, color = "#641A80") + 
    geom_bar(data = filter(topic_dt_k45_5, aws_status == "non_AWS_freq"),
           stat = "identity", aes(color = aws_status, y = -perc),
           alpha = 0, color = "#F76F5C") + 
  scale_y_continuous(breaks = seq(-0.1, 0.1, 0.025), 
                     labels = paste0(
                       as.character(c(seq(10, 0, -2.5), seq(2.5, 10, 2.5))), "%")) + 
  coord_flip(ylim = c(-0.1, 0.1)) + 
  scale_fill_viridis_d(labels = c("AWS", "non-AWS"),
                       begin = 0.3, end = 0.7, option = "magma", name = "") + 
  labs(x = "Topic", y = "Percentage of Speeches") + 
  theme(legend.position = "bottom")

ggsave("p_k45_pyramid.svg", plot = p_k45_pyramid,
       path="plots", device = "svg", width = 20, height = 20, units = "cm")

p_k45_pyramid
```


Figure \ref{k45-topic-pyramid-plot} is a pyramid plot, showing the percentage of speeches classed in each topic of AWS and non-AWS MPs. 

```{r k45-topic-bar, echo=FALSE, fig.cap="\\label{k45-topic-bar-plot}k45 Bar Chart"}
p_k45_bar <- ggplot(data = topic_dt_k45_5,
                    aes(x = assigned_topic, y = perc, fill = aws_status)) +
  geom_bar(data = topic_dt_k45_5, stat = "identity", position = "dodge") + 
  scale_y_continuous(breaks = c(0, 0.025, 0.05, 0.075),
                     labels = scales::percent) + 
  scale_fill_viridis_d(labels = c("AWS", "non-AWS"),
                       begin = 0.3, end = 0.7, option = "magma", name = "") + 
  labs(x = "Topic", y = "Percentage of Speeches") + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 90, hjust = 1))

ggsave("p_k45_bar.svg", plot = p_k45_bar,
       path="plots", device = "svg", width = 20, height = 20, units = "cm")

p_k45_bar
```

```{r stm-topic-words-k45, message=FALSE, warning=FALSE, include=FALSE}
library(tidyr)
topic_words <- labelTopics(topic_model_k45, n = 20, frexweight = 0.5)

topic_words_highest <- tibble::as_tibble(topic_words[[1]])

topic_words_highest <- topic_words_highest %>% unite(V1:V10, sep = ", ") %>%
  rename("highest" = "V1:V10")

topic_words_highest$topic <- paste0("Topic ", row.names(topic_words_highest))

topic_words_frex <- tibble::as_tibble(topic_words[[2]])

topic_words_frex <- topic_words_frex %>% unite(V1:V10, sep = ", ") %>%
  rename("FREX" = "V1:V10")

topic_words_frex$topic <- paste0("Topic ", row.names(topic_words_frex))

topic_words2 <- topic_words_highest %>% left_join(topic_words_frex) %>% 
  select(topic, everything()) %>%
  mutate(topic = recode(topic,
                        "Topic 1" = "Business (Topic 1)",
                        "Topic 2" = "Roads (Topic 2)",
                                  "Topic 3" = "Members (Topic 3)",
                                  "Topic 4" = "Gender (Topic 4)",
                                  "Topic 5" = "Housing (Topic 5)",
                                  "Topic 6" = "Questions (Topic 6)",
                                  "Topic 7" = "Technology (Topic 7)",
                                  "Topic 8" = "Food & farming (Topic 8)",
                                  "Topic 9" = "Animals (Topic 9)",
                                  "Topic 10" = "Disease (Topic 10)",
                                  "Topic 11" = "Parties (Topic 11)",
                                  "Topic 12" = "Health Care (Topic 12)",
                                  "Topic 13" = "Disasters (Topic 13)",
                                  "Topic 14" = "Energy (Topic 14)",
                                  "Topic 15" = "Volunteering (Topic 15)",
                                  "Topic 16" = "Infrastructure (Topic 16)",
                                  "Topic 17" = "Local authorities (Topic 17)",
                                  "Topic 18" = "Universities & skills (Topic 18)",
                                  "Topic 19" = "Schools (Topic 19)",
                                  "Topic 20" = "Transport (Topic 20)",
                                  "Topic 21" = "Police (Topic 21)",
                                  "Topic 22" = "Budgets & tax (Topic 22)",
                                  "Topic 23" = "Drugs (Topic 23)",
                                  "Topic 24" = "Culture & sport (Topic 24)",
                                  "Topic 25" = "Children & families (Topic 25)",
                                  "Topic 26" = "Planning & land-use (Topic 26)",
                                  "Topic 27" = "Security (Topic 27)",
                                  "Topic 28" = "Elections (Topic 28)",
                                  "Topic 29" = "Benefits & pensions (Topic 29)",
                                  "Topic 30" = "Call to action (Topic 30)",
                                  "Topic 31" = "Reports (Topic 31)",
                                  "Topic 32" = "Disability (Topic 32)",
                                  "Topic 33" = "Amendments (Topic 33)",
                                  "Topic 34" = "Justice (Topic 34)",
                                  "Topic 35" = "Military intervention (Topic 35)",
                                  "Topic 36" = "Financial system (Topic 36)",
                                  "Topic 37" = "Debate (Topic 37)",
                                  "Topic 38" = "Public bodies (Topic 38)",
                                  "Topic 39" = "Devolution (Topic 39)",
                                  "Topic 40" = "Bills (Topic 40)",
                                  "Topic 41" = "European Union (Topic 41)",
                                  "Topic 42" = "Environment (Topic 42)",
                                  "Topic 43" = "Constituency (Topic 43)",
                                  "Topic 44" = "Responses (Topic 44)",
                                  "Topic 45" = "Interventions (Topic 45)"))
```


#### Word Occurences

The table below shows the twenty most common words in each topic, and the twenty words with the highest FREX score, a measure that uses a harmonic mean of word exclusivity and topic coherence  [@airoldi2016].

```{r topic-words-table-k45, echo=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)

kable(topic_words2,  booktabs = TRUE, longtable = TRUE, 
      caption = "Words in topic - k45",
      col.names = c("Topic Number", "Top Ten Words", "Top Ten FREX")) %>%
    kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE )

```



```{r k45-topic-proportion, echo=FALSE, fig.height=7, fig.cap="\\label{k45-topic-proportion}k45 Topic Proportions"}
topic_dt_k45_3$prop <- topic_dt_k45_3$AWS_freq/topic_dt_k45_3$non_AWS_freq

topic_dt_k45_6 <- topic_dt_k45_3 %>% 
  select(assigned_topic, prop) %>%
  mutate(assigned_topic = factor(assigned_topic, 
                                 levels=c("Topic 1", "Topic 2", "Topic 3",
                                          "Topic 4", "Topic 5", "Topic 6",
                                          "Topic 7", "Topic 8", "Topic 9",
                                          "Topic 10", "Topic 11", "Topic 12", 
                                          "Topic 13", "Topic 14", "Topic 15", 
                                          "Topic 16", "Topic 17", "Topic 18", 
                                          "Topic 19", "Topic 20", "Topic 21", 
                                          "Topic 22", "Topic 23", "Topic 24", 
                                          "Topic 25", "Topic 26", "Topic 27", 
                                          "Topic 28", "Topic 29", "Topic 30",
                                          "Topic 31", "Topic 32", "Topic 33",
                                          "Topic 34", "Topic 35", "Topic 36",
                                          "Topic 37", "Topic 38", "Topic 39",
                                          "Topic 40", "Topic 41", "Topic 42",
                                          "Topic 43", "Topic 44", "Topic 45")),
          assigned_topic = recode(assigned_topic,
                                  "Topic 1" = "Business",
                                  "Topic 2" = "Roads",
                                  "Topic 3" = "Members",
                                  "Topic 4" = "Gender",
                                  "Topic 5" = "Housing",
                                  "Topic 6" = "Questions",
                                  "Topic 7" = "Technology",
                                  "Topic 8" = "Food & farming",
                                  "Topic 9" = "Animals",
                                  "Topic 10" = "Disease",
                                  "Topic 11" = "Parties",
                                  "Topic 12" = "Health Care",
                                  "Topic 13" = "Disasters",
                                  "Topic 14" = "Energy",
                                  "Topic 15" = "Volunteering",
                                  "Topic 16" = "Infrastructure",
                                  "Topic 17" = "Local authorities",
                                  "Topic 18" = "Universities & skills",
                                  "Topic 19" = "Schools",
                                  "Topic 20" = "Transport",
                                  "Topic 21" = "Police",
                                  "Topic 22" = "Budgets & tax",
                                  "Topic 23" = "Drugs",
                                  "Topic 24" = "Culture & sport",
                                  "Topic 25" = "Children & familiesies",
                                  "Topic 26" = "Planning & land-use",
                                  "Topic 27" = "Security",
                                  "Topic 28" = "Elections",
                                  "Topic 29" = "Benefits & pensions",
                                  "Topic 30" = "Call to action",
                                  "Topic 31" = "Reports",
                                  "Topic 32" = "Disability",
                                  "Topic 33" = "Amendments",
                                  "Topic 34" = "Justice",
                                  "Topic 35" = "Military intervention",
                                  "Topic 36" = "Financial system",
                                  "Topic 37" = "Debate",
                                  "Topic 38" = "Public bodies",
                                  "Topic 39" = "Devolution",
                                  "Topic 40" = "Bills",
                                  "Topic 41" = "European Union",
                                  "Topic 42" = "Environment",
                                  "Topic 43" = "Constituency",
                                  "Topic 44" = "Responses",
                                  "Topic 45" = "Interventions"),
         assigned_topic = as.character(assigned_topic),
         prop = if_else(prop < 1, 
                        (1 - prop) * -1, 
                        prop - 1)) %>%
  arrange(prop)

topic_dt_k45_6$assigned_topic <- reorder(topic_dt_k45_6$assigned_topic, topic_dt_k45_6$prop)

p_k45_prop <- ggplot(data = topic_dt_k45_6, 
                     aes(x = assigned_topic,
                         y = prop, fill = prop)) +
  geom_bar(stat = "identity") + 
  scale_y_continuous() + 
  scale_fill_viridis_c(name = "") + 
  coord_flip() + 
  labs(x = "Topic", 
       y = "Proportion of speeches made by AWS MPs (right side)\nrelative to non-AWS MPs (left side)") + 
  theme(legend.position = "bottom")

ggsave("p_k45_prop.svg", plot = p_k45_prop,
       path="plots", device = "svg", width = 20, height = 20, units = "cm")

p_k45_prop
```



### Full topic model summary - k45


```{r topic-model-k45-summary, echo=FALSE, message=FALSE}
summary(topic_model_k45)
```

### Full topic model estimate summary - k45

```{r topic-model-k45-est-summary, echo=FALSE, message=FALSE}
summary(prep_k45)
```

