---
title: "All Women Shortlists Methodology"
editor_options:
  chunk_output_type: console
link-citations: yes
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
bibliography: women.bib
---

# Methodology

Previous research on gender differences in political speech patterns has focused on differences between male and female politicians [@yu2014] or on variations in Hilary Clinton's speech patterns [@jones2016; @bligh2010].

To account for the possible effects of age, parliamentary experience and cohort, and in order to compare women selected through all women shortlists to women who were not (but theoretically had the possibility to contest all-women shortlists), speech analysis has been restricted only to Labour MPs elected during or after the 1997 General Election, and before the 2017 General Election. Words contained in parentheses were removed, as they are added by Hansard to provide additional information not actually spoken by the MP.[^1] Speeches and MP data is from a previously assembled dataset [@odell2018]. Information on candidates selected through all women shortlists is from the House of Commons Library [@kelly2016]. Unsuccessful General Election candidates selected through all women shortlists who were subsequently elected in a byelection are classified as having been selected on an all women shortlist. 

Word classification used the `Linguistic Inquiry and Word Count 2015` (LIWC) dictionary [@pennebaker2015] and tokenising tools from the `Quanteda` R package [@benoit2018]. Word counts and words-per-sentence were calculated using `stringi` [@gagolewski2018], a wrapper to the ICU regex library.

Following Yu [-@yu2014] drawing on [@newman2008] we used the following LIWC categories:

<!-- Feminine: -->
* All Pronouns (pronoun)
* First person singular pronouns (i) 
* Verbs (verb)
* Auxiliary verbs (auxverb) 
* Social processes (social) 
* Positive emotions (posemo) 
* Negative emotions (negemo) 
* Tentative words (tentat)
<!-- Masculine: -->
* Words longer than six letters (Sixltr)
* First person plural pronouns (we)
* Articles (article) 
* Prepositions (preps) 
* Anger words (anger)
* Swear words (swear)
* Cognitive processes (cogproc)

We also included words-per-sentence (WPS), total word count (WC) and Flesch–Kincaid grade level (FK) [@kincaid1975], calculated using `Quanteda` [@benoit2018] and `stringi` [@gagolewski2018].

<!--## Corpus creation -->

```{r Extracing-post-1997-Labour-speeches, eval=FALSE, include=FALSE}
### Extracing post-1997 Labour speeches
library(readr)
library(dplyr)
library(quanteda)
library(readxl)
library(lubridate)
library(stringi)

all_speech <- read_rds("senti_df2.rds")

all_speech$eo_id <- rownames(all_speech)

## Binned into quarters of a year
all_speech$y_since_start <- round(time_length(all_speech$speech_date -
                                          as.Date(all_speech$house_start_date),
                                        unit = "years")* 4)/4

lab_speech <- filter(all_speech, party_group=="Labour", 
                     house_start_date >= "1997-05-01",
                     speech_date >= "1997-05-01", 
                     speech_date < "2017-06-08", word_count > 0)

rm(all_speech)

all_women97_15 <- read_excel("list-of-mps.xlsx")

lab_speech$short_list <- lab_speech$mnis_id %in% all_women97_15$mnis

lab_speech$speech <- stri_replace_all_regex(lab_speech$speech, "\\s\\(.*?\\)",
                                            "", vectorize_all = TRUE)

write_rds(lab_speech, "lab_speech.rds")

lab_corpus <- corpus(lab_speech, docid_field = "eo_id", text_field = "speech")

write_rds(lab_corpus, "lab_corpus.rds")
```

<!--### Descriptive Statistics -->

```{r eval=FALSE, include=FALSE}
elections <- as.POSIXct(c("1997-05-01", "2001-06-07", "2005-05-05", 
               "2010-05-06", "2015-05-07", "2017-06-07"), tz = "UTC")

labour_intakes <- lab_speech %>% 
  filter(house_start_date %in% elections) %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(total=n()) 

labour_intakes_women <- lab_speech %>% 
  filter(house_start_date %in% elections, gender=="Female") %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(women=n()) 

labour_intakes <- labour_intakes %>%  left_join(labour_intakes_women)
labour_intakes$perc_women <- (labour_intakes$women/labour_intakes$total)*100

```


| General Election | Total MPs | Total Labour MPs | Total Female Labour MPs | Newly elected MPs | Intake Women | Percentage Intake Women | Intake Shortlist | Nominated Shortlist |
|---|---|---|---|---|---|---|---|---|---|
| 1997 | 659 | 418 | 101 | 177 | 64 |36% | 35 | 38 |
| 2001 | 659 | 412 | 95 | 38 | 4 | 11% | 0 | 0 |
| 2005 | 646 | 355 | 98 | 40 | 26 | 65% | 23 | 30 |
| 2010 | 650 | 258 | 81 | 64 | 32 | 50% | 28 | 63 |
| 2015 | 650 | 232 | 99 | 49 | 31 | 63% | 31 | 77 |

Data in this table is from House of Commons library reports [@kelly2016; @audickas2017]. All women shortlists were not used by Labour during the 2001 General Election.

<!--## LIWC creation-->

```{r women-v-men, eval=FALSE, include=FALSE}
#remotes::install_github("kbenoit/quanteda.dictionaries")
library(quanteda.dictionaries)
library(purrr)
library(tidyr)
library(effsize)

liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic",
       format = "LIWC")

lab_liwc <- liwcalike(lab_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

lab_liwc[["Sixltr"]] <- sapply(
  tokens(texts(lab_corpus), remove_hyphens = TRUE),
  function(y) sum(stri_length(y) > 6)) / lab_liwc[["WC"]] * 100

lab_liwc$WC <- stri_count_boundaries(lab_liwc$speech,
                                       type="word", skip_word_none=FALSE)

# lab_liwc$FK <-  textstat_readability(texts(lab_corpus), "Flesch.Kincaid")
# 
# lab_liwc$FK <- lab_liwc$FK$Flesch.Kincaid
# 
# lab_liwc$FK <- if_else(lab_liwc$WC < 5, NA_real_, lab_liwc$FK)

lab_liwc$WPS <- lab_liwc$WC/stri_count_boundaries(lab_liwc$speech,
                                       type="sentence", skip_word_none=FALSE)

lab_liwc$FK <- case_when(lab_liwc$WC >= 5 ~ 
                            0.39 * lab_liwc$WPS + 
                            11.8 * quanteda::nsyllable(lab_liwc$speech)/
                            lab_liwc$WC - 15.59, TRUE ~ NA_real_)

#lab_liwc$FK2 <- if_else(lab_liwc$WC < 5, NA_real_, lab_liwc$FK2)

lab_liwc <- lab_liwc %>% select(docname, Segment, WC, WPS, FK, everything())

#lab_liwc <- read_rds("lab_liwc.rds")

write_rds(lab_liwc, "lab_liwc.rds")
```


## Women vs Men

```{r liwc-women-men, include=FALSE}
library(readr)
library(dplyr)
library(purrr)
library(tidyr)
library(effsize)

lab_liwc <- read_rds("lab_liwc.rds")

## Group by gender, short_list, see what's up
cols <- names(lab_liwc)[4:92]

lab_liwc_men_women_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc %>%
   group_by(gender) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

#tibble::glimpse(lab_liwc_men_women_mean)

lab_liwc_men_women_tidy_mean <- gather(lab_liwc_men_women_mean, 
          "attribute", "weighted_mean", -gender, -WC) 

lab_liwc_men_women_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc %>%
   group_by(gender) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_men_women_tidy_sd <- gather(lab_liwc_men_women_sd, "attribute",
                                     "sd", -gender, -WC) 

## Joining together the SD and Means to get CIs

## Calculate Cohen's D in here somehow?
lab_liwc_men_women2 <- left_join(lab_liwc_men_women_tidy_mean, 
         lab_liwc_men_women_tidy_sd) %>% 
 left_join(lab_liwc %>% 
    group_by(gender) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

rm(lab_liwc_men_women_tidy_sd, lab_liwc_men_women_tidy_mean)

fem_mac <- c("pronoun", "i", "we", "verb", "auxverb", "social", "posemo", 
             "negemo", "tentat", "Sixltr",  "article", "prep",
             "anger", "swear", "cogproc", "WPS", "WC", "FK")

lab_liwc_men_women2_subset <- lab_liwc_men_women2 %>%
  filter(attribute %in% fem_mac)

fem_mac_df <- tibble::tibble(
  word_type = fem_mac,
  women = c(1:length(fem_mac)),
  women_sd = c(1:length(fem_mac)),
  men = c(1:length(fem_mac)),
  men_sd = c(1:length(fem_mac)),
  cohen_d = c(1:length(fem_mac)),
  magnitude = c(1:length(fem_mac)))

for (i in fem_mac) {
  d <- (cohen.d(lab_liwc[[i]], lab_liwc$gender, na.rm = TRUE,
                noncentral = FALSE, pooled = TRUE))
  fem_mac_df$women[fem_mac_df$word_type==i] <- mean(lab_liwc[lab_liwc$gender == "Female", i], na.rm = TRUE)
  fem_mac_df$men[fem_mac_df$word_type==i] <- mean(lab_liwc[lab_liwc$gender == "Male", i], na.rm = TRUE)
  fem_mac_df$women_sd[fem_mac_df$word_type==i] <- sd(lab_liwc[lab_liwc$gender == "Female", i], na.rm = TRUE)
  fem_mac_df$men_sd[fem_mac_df$word_type==i] <- sd(lab_liwc[lab_liwc$gender == "Male", i], na.rm = TRUE)
  fem_mac_df$cohen_d[fem_mac_df$word_type==i] <- (d$estimate[[1]])
  fem_mac_df$magnitude[fem_mac_df$word_type==i] <- as.character(d$magnitude[[1]])
}

#fem_mac_df

fem_mac_df$word_type <- recode(fem_mac_df$word_type,
               "pronoun" = "All Pronouns",
               "i" = "First person singular pronouns",
               "verb" = "Verbs",
               "auxverb" = "Auxiliary verbs",
               "social" = "Social processes ",
               "posemo" = "Positive emotions",
               "negemo" = "Negative emotions",
               "tentat" = "Tentative words",
               "Sixltr" = "More than six letters",
               "we" = "First person plural pronouns",
               "article" = "Articles",
               "prep" = "Prepositions",
               "anger" = "Anger words",
               "swear" = "Swear words",
               "cogproc" = "Cognitive processes",
               "WPS" = "Words per Sentence",
               "WC" = "Total Word Count",
               "FK" = "Flesh-Kincaid Grade Level")

### Maybe do something different instead of this?
# library(ggplot2)
# 
# p_men_women <- ggplot(aes(y = weighted_mean, x = gender),
#                       data = lab_liwc_men_women2_subset) +
#   geom_col() +
#   geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci),
#                 width = 0.2) +
#   facet_wrap(~attribute)
# 
# p_men_women

```

```{r, echo=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)
kable(fem_mac_df, digits = 2, 
      caption = "Effect Sizes for Male and Female Labour MPs",
      col.names = c("", "Mean", "SD", "Mean", "SD", "Cohen's D", "Magnitude") )  %>%
  kable_styling() %>% 
  add_header_above(c(" " = 1, "Women" = 2, "Men" = 2, "Effect Size" = 2))

```


There are no categories where gender differences meet the effect size threshold of $|0.2|$ suggested by Cohen [-@cohen1988, 25--26] to indicate a small effect. 4 categories -- words with more than six letters, prepositions, words-per-sentence and Flesh-Kincaid grade level -- exceeded the $|0.1|$ threshold suggested by Newman et al [-@newman2008].


## Shortlists vs Non-Shortlists

```{r liwc-shortlists, include=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(effsize)

lab_liwc <- read_rds("lab_liwc.rds")

lab_liwc_women <- filter(lab_liwc, gender=="Female",
                         house_start_date >= "1997-05-01")

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc_women)[4:92]

lab_liwc_women_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_women %>%
   group_by(gender, short_list, y_since_start) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_women_tidy_mean <- gather(lab_liwc_women_mean, "attribute",
                                   "weighted_mean", -short_list, -gender, -WC,
                                   -y_since_start) 

lab_liwc_women_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc_women %>%
   group_by(gender, short_list, y_since_start) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_women_tidy_sd <- gather(lab_liwc_women_sd, "attribute",
                                 "sd", -short_list, -gender, -WC,
                                 -y_since_start) 

## Joining together the SD and Means to get CIs
lab_liwc_women2 <- left_join(lab_liwc_women_tidy_mean,
                             lab_liwc_women_tidy_sd) %>% 
 left_join(lab_liwc_women %>% 
    group_by(gender, short_list, y_since_start) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

lab_liwc_women2_subset <- lab_liwc_women2 %>%
  filter(attribute %in% fem_mac)

# library(ggplot2)
# 
# p1 <- ggplot(aes(y = weighted_mean, x = y_since_start, 
#                  group = short_list, colour = short_list),
#                       data = lab_liwc_women2_subset) +
#   geom_smooth() + 
#   geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci),
#                 width = 0.2) +
#   facet_wrap(~attribute)
# 
# p1

```

```{r, echo=FALSE,results = 'asis'}
fem_mac_df_sl <- tibble::tibble(
  word_type = fem_mac,
  short_list = c(1:length(fem_mac)),
  short_list_sd = c(1:length(fem_mac)),
  non_short_list = c(1:length(fem_mac)),
  non_short_list_sd = c(1:length(fem_mac)),
  cohen_d = c(1:length(fem_mac)),
  magnitude = c(1:length(fem_mac)))

lab_liwc_women$short_list <- as.factor(lab_liwc_women$short_list)

for (i in fem_mac) {
  d <- (cohen.d(lab_liwc_women[[i]], lab_liwc_women$short_list, na.rm = TRUE,
                noncentral = FALSE, pooled = TRUE))
  fem_mac_df_sl$short_list[fem_mac_df_sl$word_type==i] <-
    mean(lab_liwc_women[lab_liwc_women$short_list == TRUE, i], na.rm = TRUE)
  fem_mac_df_sl$non_short_list[fem_mac_df_sl$word_type==i] <- 
    mean(lab_liwc_women[lab_liwc_women$short_list == FALSE, i], na.rm = TRUE)
  fem_mac_df_sl$short_list_sd[fem_mac_df_sl$word_type==i]  <- 
      sd(lab_liwc_women[lab_liwc_women$short_list == TRUE, i], na.rm = TRUE)
  fem_mac_df_sl$non_short_list_sd[fem_mac_df_sl$word_type==i] <- 
    sd(lab_liwc_women[lab_liwc_women$short_list == FALSE, i], na.rm = TRUE)
  fem_mac_df_sl$cohen_d[fem_mac_df_sl$word_type == i] <- 
    d$estimate[[1]]
  fem_mac_df_sl$magnitude[fem_mac_df_sl$word_type == i] <-
    as.character(d$magnitude[[1]])
}

fem_mac_df_sl$word_type <- recode(fem_mac_df_sl$word_type,
               "pronoun" = "All Pronouns",
               "i" = "First person singular pronouns",
               "verb" = "Verbs",
               "auxverb" = "Auxiliary verbs",
               "social" = "Social processes ",
               "posemo" = "Positive emotions",
               "negemo" = "Negative emotions",
               "tentat" = "Tentative words",
               "Sixltr" = "More than six letters",
               "we" = "First person plural pronouns",
               "article" = "Articles",
               "prep" = "Prepositions",
               "anger" = "Anger words",
               "swear" = "Swear words",
               "cogproc" = "Cognitive processes",
               "WPS" = "Words per Sentence",
               "WC" = "Total Word Count",
               "FK" = "Flesh-Kincaid Grade Level")

```

```{r, echo=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)
kable(fem_mac_df_sl, digits = 2, 
      caption = "Effect Sizes for Female Labour MPs by selection process",
      col.names = c("", "Mean", "SD", "Mean", "SD",
                    "Cohen's D", "Magnitude")) %>%
  kable_styling() %>% 
  add_header_above(c(" " = 1, "All Women Shortlists" = 2,
                     "Open Shorlists" = 2, "Effect Size" = 2))

```


There are no categories among female Labour MPs by selection process meeting the $|0.2|$ threshold. Only one category -- first person plural pronouns, _d_=0.19 -- exceeded $|0.1|$.


## Spacy

```{r eval=FALSE, include=FALSE}
library(spacyr)
library(progress)

lab_speech <- read_rds("lab_speech.rds")

lab_speech$year <- as.factor(lab_speech$year)

split_data <- split(lab_speech, lab_speech$year) ### Splitting data variable

all_names <- names(split_data)

pb_save <- progress_bar$new(total = length(all_names),
                            format = "[:bar] :percent ETA: :eta Elapsed: :elapsedfull")

for (this_name in all_names) {
  save_name <- paste0(this_name, "x.rds")
  write_rds(split_data[[this_name]], path = save_name)
  pb_save$tick()
}


# 
# lab_corpus_sample <- corpus(lab_speech_sample,
#                             docid_field = "eo_id", text_field = "speech")
# 
# system.time(
#   lab_annotate_sample <- spacy_parse(lab_corpus_sample, tag = TRUE,
#                                    dependency = TRUE,  lemma = FALSE,
#                                    pos = FALSE) # need to use lab_corpus for this
# )


#devtools::install_github("quanteda/spacyr")
#spacy_install(python_path = "/Users/evanodell/Documents/anaconda3/bin/python3")
spacy_initialize()

atemp <- list.files(pattern = "*x.rds")

pb <- progress_bar$new(total = length(atemp), 
                       format = "[:bar] :percent ETA: :eta Elapsed: :elapsedfull\n")

for (i in atemp) {
   pb$tick(0)
  
  df <- read_rds(i)
  
  message(cat("Corpusising "), i, "\n")
  
  lab_corpus <- corpus(df, docid_field = "eo_id", text_field = "speech")
  
  i <- gsub("x.rds", "", i)
  
  message(cat("Annotating "), i, "\n")
  
  # need to use corpus object for this
  lab_annotate <- spacy_parse(lab_corpus, tag = TRUE, dependency = TRUE,
                            lemma = FALSE, pos = FALSE, entity = TRUE) 
 
  save_name <- paste0("./annotated/ano_", i, ".rds")
  
  write_rds(lab_annotate, path = save_name)
  
  pb$tick()
  
  gc()

}

atemp2 <- list.files("./annotated/", pattern = "*.rds")

atemp2 <- paste0("annotated/", atemp2)

df.list <- sapply(atemp2, read_rds, simplify = FALSE)

annotated_labour <- bind_rows(df.list)

rm(df.list, atemp2)

write_rds(annotated_labour, "annotated_labour.rds")

### Calculate the number of different parts of speech



```



```{r eval=FALSE, include=FALSE}
# !diagnostics off
library(readr)
library(dplyr)
annotated_labour <- read_rds("annotated_labour.rds")

post_df <- tibble::tribble(
     ~tag,    ~POS,
  "-LRB-", "PUNCT",
  "-RRB-", "PUNCT",
      ",", "PUNCT",
      ":", "PUNCT",
      ".", "PUNCT",
     "''", "PUNCT",
   "\"\"", "PUNCT",
     "``", "PUNCT",
      "$",   "SYM",
    "ADD",     "X",
    "AFX",   "ADJ",
    "BES",  "VERB",
     "CC",  "CONJ",
     "CD",   "NUM",
     "DT",   "DET",
     "EX",   "ADV",
     "FW",     "X",
     "GW",     "X",
    "HVS",  "VERB",
   "HYPH", "PUNCT",
     "IN",   "ADP",
     "JJ",   "ADJ",
    "JJR",   "ADJ",
    "JJS",   "ADJ",
     "LS", "PUNCT",
     "MD",  "VERB",
    "NFP", "PUNCT",
    "NIL",    "NA",
     "NN",  "NOUN",
    "NNP", "PROPN",
   "NNPS", "PROPN",
    "NNS",  "NOUN",
    "PDT",   "ADJ",
    "POS",  "PART",
    "PRP",  "PRON",
   "PRP$",   "ADJ",
     "RB",   "ADV",
    "RBR",   "ADV",
    "RBS",   "ADV",
     "RP",  "PART",
    "_SP", "SPACE",
    "SYM",   "SYM",
     "TO",  "PART",
     "UH",  "INTJ",
     "VB",  "VERB",
    "VBD",  "VERB",
    "VBG",  "VERB",
    "VBN",  "VERB",
    "VBP",  "VERB",
    "VBZ",  "VERB",
    "WDT",   "ADJ",
     "WP",  "NOUN",
    "WP$",   "ADJ",
    "WRB",   "ADV",
     "XX",     "X"
  )

post_df$POS <- as.factor(post_df$POS)

annotated_labour <- annotated_labour %>% left_join(post_df)

summary(annotated_labour)

write_rds(annotated_labour, "annotated_labour.rds")

```

## POS Analysis


```{r tidying-annotations, eval=FALSE, include=FALSE}
library(readr)
library(dplyr)
library(magrittr)
library(tidyr)
library(effsize)

annotated_labour <- read_rds("annotated_labour.rds")

annotated_labour <- annotated_labour %>% 
  filter(POS != "PUNCT", is.na(POS) == FALSE, POS != "SPACE") %>%
  group_by(doc_id, tag) %>%
  summarise(count = n()) %>%
  mutate(freq = count / sum(count)) %>% ungroup() 

annotated_labour$count <- NULL

annotated_labour <- annotated_labour %>% spread(tag, freq)

lab_speech <- read_rds("lab_speech.rds")

annotated_labour <- annotated_labour %>% left_join(select(lab_speech, eo_id, gender, short_list), by = c("doc_id"="eo_id"))

d <- cohen.d(annotated_labour$NNS, annotated_labour$gender, na.rm = TRUE)


```



## Tokenising / Keyness

The most commonly used words by both men and women would be protocol boilerplate expressions, so we calculate the keyness of words to identify gender differences in the choices of topics raised by men and women, and by short-list and non-shortlist women.

### Men vs Women

```{r gender-keyness, echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(quanteda)
library(ggplot2)

#lab_tokens <- tokens(lab_corpus, what = "word", include_docvars = TRUE,
#      remove_punct = TRUE)### Do something to only include the short_list and gender docvars

lab_corpus <- read_rds("lab_corpus.rds")

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister") ## Need to remove constituency names from this

lab_dfm_key <- lab_corpus %>% 
  dfm(remove = parliament_stopwords, remove_punct = TRUE,
      verbose = TRUE, groups = "gender") %>%
  dfm_weight("count")

lab_keyness <- textstat_keyness(lab_dfm_key, measure = c("chi2"))

#head(lab_keyness)

lab_keyness_plot <- textplot_keyness(lab_keyness, n=15) +  
  coord_cartesian(xlim=c(-5000, 14800)) +
  labs(title = "Keyness in Labour MPs by Gender",
       x = "Chi2")


lab_keyness_plot
## Figure out what the fuck is up with Hull?
```

Keyness -- a linguistic measure of the frequency of different words in two groups of texts -- reveals clear gender differences in the most disproportionately common words used by female and male Labour MPs. Unsurprisingly, despite male MPs saying almost twice as many words (30601887 vs 15898845) <!--Double-check these numbers--> as their female colleagues, female Labour MPs were more than two-and-a-half (2.61) times as likely to say "women". They were also much more likely to refer to "women's" and "woman". Female Labour MPs also appear much more likely to discuss "children", "people", "care", "families", "home", "parents", "work" and social policy areas such as "services", "disabled [people]" and "housing" than their male colleagues. Male MPs were more likely to refer to military topics ("Iraq", "nuclear"), and to parliamentary process and protocol  -- "question", "political", "conservative", "electoral", "house", "party", "argument" "liberal" and "point" are far more common in speeches by male Labour MPs than by female ones. This could suggest that male MPs are more comfortable using the traditional language of House of Commons debate.


### Shortlists vs Non-Shortlists


```{r shortlist-keyness, echo=FALSE, message=FALSE, warning=FALSE}

lab_corpus_fem <- corpus_subset(lab_corpus, gender=="Female")

lab_dfm_key_fem <- lab_corpus_fem %>% 
  dfm(remove = parliament_stopwords, remove_punct = TRUE,
      verbose = TRUE, groups = "short_list") %>%
  dfm_weight("count")

lab_keyness_fem <- textstat_keyness(lab_dfm_key_fem, measure = c("chi2"))

#head(lab_keyness_fem)

fem_keyness_plot <- textplot_keyness(lab_keyness_fem, n=15) + 
  coord_cartesian(xlim=c(-1700,1000)) +
  labs(title = "Keyness in Female Labour MPs by Selection Process",
       x = "Chi2")

fem_keyness_plot

```


Keyness differences by selection process are not as obviously stereotypical. Nonetheless, the most common words amongst AWS MPs included "carers", "disabled", "bedroom" and "sen"[^2]. [AWS MPs given policy briefs related to these areas? Seeking them out?]


[^1]: e.g. a reference to "the member for Bethnal Green and Bow" in keeping with Parliamentary convention of identifying MPs by their seat rather than their name would be followed by "(Rushnara Ali)".

[^2]: Special Educational Needs