---
title: "All Women Shortlists Scratchpad"
output: html_notebook
bibliography: women.bib
link-citations: true
---

Existing work on this topic has either compared women and men, or tracked changes in a single woman [@jones2016] or group of women. 


### Extracing post-1997 Labour speeches

```{r}
library(readr)
library(dplyr)
library(quanteda)
library(readxl)
library(lubridate)

all_speech <- read_rds("senti_df2.rds")

## Binned into quarters of a year
all_speech$y_since_start <- round(time_length(all_speech$speech_date -
                                          as.Date(all_speech$house_start_date),
                                        unit = "years")* 4)/4

lab_speech <- filter(all_speech, party_group=="Labour", 
      speech_date >= "1997-05-01", speech_date < "2017-06-08", word_count > 0)

rm(all_speech)

all_women97_15 <- read_excel("list-of-mps.xlsx")

lab_speech$short_list <- lab_speech$mnis_id %in% all_women97_15$mnis

#library(stringi)
## Pattern replacing part 1
# (try to do this vectorised style?)
# lab_speech$speech <- stri_replace_all_regex(lab_speech$speech, '(?:\\srt\\s|\\srt.\\s|\\sright\\s){1}(?:hon\\s|hon.\\s|honourable\\s){1}',
#                                             " Right Honourable ")
# 
# lab_speech$speech <- stri_replace_all_regex(lab_speech$speech, 
#                                             '(?:\\shon\\s|\\shon.\\s){1}', 
#                                             " Honourable ")
# 
# ### This is next bit doesn't work, not sure why that is
# lab_speech$speech <- stri_replace_all_regex(lab_speech$speech,   '(?:(?:right\\s){0,1}(?:honourable\\s|noble\\s){1}(?:(?:and\\s)|(?:lord\\s)|(?:honourable\\s)|(?:learned\\s)|(?:gallant\\s)|(?:noble\\s)|(?:respected\\s)|(?:reverend\\s)){0,4}(?:the\\s){0,1}(?:(?:lord(?:s){0,1})|(?:justice(?:s){0,1}\\b)|(?:gentle\\sm[ea]n(?:t){0,1})|(?:gentlem[ea]n(?:t){0,1})|(?:friend(?:s){0,1}\\b)|(?:member(?:s){0,1}\\b)|(?:lad(?:y|(?:ies)){1})){1})',"formal_title")
# 
# test <- gsub('(?:(?:right\\s){0,1}(?:honourable\\s|noble\\s){1}(?:(?:and\\s)|(?:lord\\s)|(?:honourable\\s)|(?:learned\\s)|(?:gallant\\s)|(?:noble\\s)|(?:respected\\s)|(?:reverend\\s)){0,4}(?:the\\s){0,1}(?:(?:lord(?:s){0,1})|(?:justice(?:s){0,1}\\b)|(?:gentle\\sm[ea]n(?:t){0,1})|(?:gentlem[ea]n(?:t){0,1})|(?:friend(?:s){0,1}\\b)|(?:member(?:s){0,1}\\b)|(?:lad(?:y|(?:ies)){1})){1})',"formal_title", lab_speech$speech)

lab_corpus <- corpus(lab_speech, docid_field = "eo_id", text_field = "speech")
```




# Descriptive Statistics

```{r eval=FALSE, include=FALSE}
elections <- as.POSIXct(c("1997-05-01", "2001-06-07", "2005-05-05", 
               "2010-05-06", "2015-05-07", "2017-06-07"), tz = "UTC")

labour_intakes <- lab_speech %>% 
  filter(house_start_date %in% elections) %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(total=n()) 

labour_intakes_women <- lab_speech %>% 
  filter(house_start_date %in% elections, gender=="Female") %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(women=n()) 

labour_intakes <- labour_intakes %>%  left_join(labour_intakes_women)
labour_intakes$perc_women <- (labour_intakes$women/labour_intakes$total)*100

```


- Statistics on the gender of Labour MPs in each general election:

| General Election | Total MPs | Total Labour MPs | Total Female Labour MPs | Newly elected MPs | Intake Women | Percentage Intake Women | Intake Shortlist | Nominated Shortlist |
|---|---|---|---|---|---|---|---|---|---|
| 1997 | 659 | 418 | 101 | 177 | 64 |36% | 35 | 38 |
| 2001 | 659 | 412 | 95 | 38 | 4 | 11% | 0 | 0 |
| 2005 | 646 | 355 | 98 | 40 | 26 | 65% | 23 | 30 |
| 2010 | 650 | 258 | 81 | 64 | 32 | 50% | 28 | 63 |
| 2015 | 650 | 232 | 99 | 49 | 31 | 63% | 31 | 77 |

Stats from [@kelly2016] and [@audickas2017]. All women shortlists were not used for the 2001 General Election




### Load women speeches

All women shortlists are from house of commons library [@kelly2016]

Hypothesis:
- Women selected through all women shortlists use more "feminine" language -- pronouns, particular personal pronouns, passive voice, hedges, etc -- than women selected in open selections.

Plan of attack:

- Use one of the `cleanNLP` packages to get everything running.
- Group by election, party, only include women elected after 1997?
- Check Jones2016 for more info
- Group by cohort and intake



### Women vs Men

```{r}
#remotes::install_github("kbenoit/quanteda.dictionaries")
library(quanteda.dictionaries)
library(purrr)
library(tidyr)

liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic",
       format = "LIWC")

lab_liwc <- liwcalike(lab_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

lab_liwc[["Sixltr"]] <- sapply(quanteda::tokens(texts(lab_corpus), remove_hyphens = TRUE), function(y) sum(stringi::stri_length(y) > 6)) / lab_liwc[["WC"]] * 100

#write_rds(lab_liwc, "lab_liwc.rds")

lab_liwc <- read_rds("lab_liwc.rds")

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc)[4:91]

lab_liwc_men_women_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc %>%
   group_by(gender) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

#tibble::glimpse(lab_liwc_men_women_mean)

lab_liwc_men_women_tidy_mean <- gather(lab_liwc_men_women_mean, 
          "attribute", "weighted_mean",
          -gender, -WC) 

lab_liwc_men_women_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc %>%
   group_by(gender) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_men_women_tidy_sd <- gather(lab_liwc_men_women_sd, "attribute",
          "sd", -gender, -WC) 

## Joining together the SD and Means to get CIs

## Calculate Cohen's D in here somehow?
lab_liwc_men_women2 <- left_join(lab_liwc_men_women_tidy_mean, 
         lab_liwc_men_women_tidy_sd) %>% 
 left_join(lab_liwc %>% 
    group_by(gender) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

rm(lab_liwc_men_women_tidy_sd, lab_liwc_men_women_tidy_mean)

fem_mac <- c("pronoun", "i", "verb", "auxverb", "social", "posemo", 
             "negemo", "cogmech", "tentat", "Sixltr", "we", 
             "article", "prep", "anger", "swear")

lab_liwc_men_women2_subset <- lab_liwc_men_women2 %>%
  filter(attribute %in% fem_mac)

#devtools::install_github("tidyverse/ggplot2")
library(ggplot2)

p_men_women <- ggplot(aes(y = weighted_mean, x = gender),
                      data = lab_liwc_men_women2_subset) + 
  geom_col() + 
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci),
                width = 0.2) +
  facet_wrap(~attribute)

p_men_women

### Maybe do something different instead of this?

lmtest <- lm(pronoun ~ gender, data = lab_liwc)

library(effsize)

cohen.d.default(lab_liwc, lab_liwc$gender, noncentral = TRUE)


## Is this the right thing to be doing here?
test <- lapply((lab_liwc)[4:79], cohen.d, lab_liwc$gender, pooled = TRUE,
       na.rm = TRUE, noncentral = TRUE)

```




### Shortlists vs Non-Shortlists

```{r}
#liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic", format = "LIWC")

lab_speech_women <- filter(lab_speech, gender=="Female", 
                           speech_date >= "1997-05-01", 
                           speech_date < "2017-06-08", word_count > 0)

lab_women_corpus <- corpus(lab_speech_women, docid_field = "eo_id",
                           text_field = "speech")

lab_liwc_women <- liwcalike(lab_women_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc_women)[4:91]

lab_liwc_women_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_women %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

tibble::glimpse(lab_liwc_women_mean)

lab_liwc_women_tidy_mean <- gather(lab_liwc_women_mean, "attribute",
                                   "weighted_mean", -short_list, -gender, -WC) 


lab_liwc_women_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc_women %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_women_tidy_sd <- gather(lab_liwc_women_sd, "attribute",
                                 "sd", -short_list, -gender, -WC) 

## Joining together the SD and Means to get CIs
lab_liwc_women2 <- left_join(lab_liwc_women_tidy_mean,
                             lab_liwc_women_tidy_sd) %>% 
 left_join(lab_liwc_women %>% 
    group_by(gender, short_list) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)
```



### Shortlists vs Non-Shortlists vs Men

```{r}
liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic", format = "LIWC")

lab_liwc <- liwcalike(lab_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc)[4:91]

lab_liwc_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

tibble::glimpse(lab_liwc_mean)

lab_liwc_tidy_mean <- gather(lab_liwc_mean, "attribute", "weighted_mean",
        -short_list, -gender, -WC) 


lab_liwc_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_tidy_sd <- gather(lab_liwc_sd, "attribute", "sd", -short_list,
        -gender, -WC) 

## Joining together the SD and Means to get CIs
lab_liwc2 <- left_join(lab_liwc_tidy_mean, lab_liwc_tidy_sd) %>% 
 left_join(lab_liwc %>% 
    group_by(gender, short_list) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

```

#### Masculine and Feminine thingys
Feminine: 
  - pronoun
  - i 
  - verb
  - auxverb 
  - social 
  - posemo 
  - negemo 
  - cogmech
  - tentat
  
Masculine:
  - Sixltr
  - we
  - article 
  - preps 
  - anger
  - swear

### Do the same thing as above, but this time only with MPs elected in 1997 or onwards



### Tokenising 

```{r}
### Need to strip out all that crap refering to constituencies and decorum currently stored in perl script
lab_tokens <- tokens(lab_corpus, what = "word", include_docvars = TRUE,
      remove_punct = TRUE)### Do something to only include the short_list and gender docvars

lab_dfm <- dfm(lab_tokens, remove = stopwords("english"), verbose = TRUE)

lab_freq <- textstat_frequency(lab_dfm, groups = c("short_list", "gender"))

lab_keyness <- textstat_keyness(lab_dfm) ## this isn't working the way I want it to. Going off the wrong docvar?

```



### Experiment in plotting

```{r}

lab_liwc_lg_mean_no_min <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_lg %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_lg_tidy_mean_no_min <- gather(lab_liwc_lg_mean_no_min, "attribute", 
         "weighted_mean", -short_list, -gender, -WC) 


p0 <- ggplot(aes(y = weighted_mean, x = attribute,
     group = interaction(gender, short_list)),
    data=filter(lab_liwc_lg_tidy_mean_no_min,
       attribute != "WPS", attribute != "AllPunc")) + 
 geom_col(position = "dodge", aes(fill=gender))

p0

```






### liwc with LG dictionary

Using [@benoit2018] with `liwcalike` function from the `quanteda.dictionaries` package

```{r}
#lab_dfm <- dfm(lab_corpus, groups = c("short_list", "gender"))

#lab_dist <- textstat_dist(lab_dfm, selection = NULL, margin = "features",
# method = "euclidean", upper = FALSE, diag = FALSE, p = 2)

## Interesting dictionary
lab_liwc_lg <- liwcalike(lab_corpus, 
      dictionary = data_dictionary_LaverGarry, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

cols <- names(lab_liwc_lg)[4:37]

lab_liwc_lg_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_lg %>%
   group_by(gender, short_list, ministry) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

tibble::glimpse(lab_liwc_lg_mean)

lab_liwc_lg_tidy_mean <- gather(lab_liwc_lg_mean, "attribute", "weighted_mean", -short_list,
        -gender, -ministry, -WC) 


lab_liwc_lg_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc_lg %>%
   group_by(gender, short_list, ministry) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_lg_tidy_sd <- gather(lab_liwc_lg_sd, "attribute", "sd", -short_list,
        -gender, -ministry, -WC) 

## Joining together the SD and Means to get CIs
lab_liwc_lg2 <- left_join(lab_liwc_lg_tidy_mean, lab_liwc_lg_tidy_sd) %>% 
 left_join(lab_liwc_lg %>% 
 group_by(gender, short_list, ministry) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
  lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
 upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

library(ggplot2)

lab_liwc_lg2$attribute <- as.factor(lab_liwc_lg2$attribute)

## Test Case
p1 <- ggplot(aes(y = weighted_mean, x = ministry,
     group = interaction(gender, short_list)), 
    data = filter(lab_liwc_lg2, attribute == "values.conservative")) + 
 geom_line(aes(colour = gender, linetype=short_list)) + 
 geom_ribbon(aes(ymin=lower_ci,ymax=upper_ci),alpha=0.3)

p1

### ID the areas of possible difference

fem <- filter(lab_liwc_lg2, gender=="Female")


```




### Spacy

```{r}
lab_speech$year <- as.factor(lab_speech$year)

split_data <- split(lab_speech, lab_speech$year) ### Splitting data variable

all_names <- names(split_data)

for (this_name in all_names) {
  df <- corpus(split_data[[this_name]] ,
                             docid_field = "eo_id", text_field = "speech")
  save_name <- paste0(this_name, "x.rds")
  write_rds(df, path = save_name)
}


# 
# lab_corpus_sample <- corpus(lab_speech_sample,
#                             docid_field = "eo_id", text_field = "speech")
# 
# system.time(
#   lab_annotate_sample <- spacy_parse(lab_corpus_sample, tag = TRUE,
#                                    dependency = TRUE,  lemma = FALSE,
#                                    pos = FALSE) # need to use lab_corpus for this
# )

## use a loop for this?
#devtools::install_github("quanteda/spacyr")
library(spacyr)
library(progress)
spacy_install(python_path = "/Users/evanodell/Documents/anaconda3/bin/python3")
spacy_initialize()

atemp <- list.files(pattern = "*x.rds")

pb <- progress_bar$new(total = length(atemp))

for (i in atemp) {
  
  lab_corpus <- read_rds(i)
  
  i <- gsub("x.rds", "", i)
  
   # need to use corpus object for this
  lab_annotate <- spacy_parse(lab_corpus, tag = TRUE, dependency = TRUE,
                            lemma = FALSE, pos = FALSE, entity = TRUE) 
 

  save_name <- paste0("ano_", i, ".rds")
  
  write_rds(lab_annotate, path = save_name)
  
  pb$tick()

}


write_rds(lab_annotate, "lab_annotate.rds")

```

