---
title: "methods-k30"
author: "Evan Odell"
date: "06/09/2018"
output: html_document
---

### Shortlists vs Non-Shortlists - K30
```{r STM-classification-k30, eval=FALSE, include=FALSE}
library(stm)
library(readr)

lab_corpus_fem_stm <- read_rds("data/lab_corpus_fem_stm.rds")

set.seed(402)
#topic_model_k30 seed = 9957388
topic_model_k30 <- stm(lab_corpus_fem_stm$documents, 
                       vocab = lab_corpus_fem_stm$vocab, 
                       K = 60, prevalence = ~short_list, 
                       seed = 9957388,
                       data = lab_corpus_fem_stm$meta,
                       verbose = TRUE, init.type = "Spectral")

write_rds(topic_model_k30, "data/topic_model_k30.rds")
```

```{r STM-men-women-match-k30, eval=FALSE, include=FALSE}
library(readr)
library(stm)
library(viridis)
library(dplyr)
library(igraph)
library(ggplot2)
library(quanteda)
topic_model_k30 <- read_rds("data/topic_model_k30.rds")

lab_corpus <- read_rds("data/lab_corpus.rds")

#topic_model2 <- read_rds("data/stm-topic-model2.rds")

lab_corpus_man <- corpus_subset(lab_corpus, gender=="Male")

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister", "c")

rm(lab_corpus)
#ndoc(lab_corpus_fem)

lab_corpus_man_stm <- dfm(lab_corpus_man, remove_punct = TRUE,
                           remove = parliament_stopwords, verbose = TRUE) %>%
  convert(to = "stm", docvars = NULL)

#lab_corpus_man_stm$meta$short_list <- as.factor(lab_corpus_man_stm$meta$short_list)

write_rds(lab_corpus_man_stm, "data/lab_corpus_man_stm.rds")

new_man_k30 <- alignCorpus(new=lab_corpus_man_stm, old.vocab=topic_model_k30$vocab)

#new_man <- asSTMCorpus(new_man)

topic_model_man <- fitNewDocuments(model = topic_model_k30, 
                                   documents = new_man_k30$documents,
                                   newData = new_man_k30$meta, 
                                   prevalence = ~short_list, verbose = TRUE)

write_rds(topic_model_man_k30, "data/topic_model_man.rds")
write_rds(new_man_k30, "data/new_man_k30.rds")
```

```{r corr_creation-k30, eval=FALSE, include=FALSE}
library(readr)
library(stm)
library(viridis)
library(dplyr)
library(igraph)
library(ggplot2)
library(quanteda)
topic_model_k30 <- read_rds("data/topic_model_k30.rds")

lab_corpus_fem_stm <- read_rds("data/lab_corpus_fem_stm.rds")

corr_topic_k30 <- topicCorr(topic_model_k30, method = "huge", verbose = FALSE)

prep_k30 <- estimateEffect(1:30 ~ short_list, topic_model_k30, 
                       meta = lab_corpus_fem_stm$meta, uncertainty = "Global")

write_rds(corr_topic_k30, "data/corr_topic_k30.rds")

write_rds(prep_k30, "data/prep_k30.rds")
```

```{r stm-analysis-k30, echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.cap="\\label{k30-network}Fruchterman-Reingold plot of K30 Network"}
library(readr)
library(stm)
library(viridis)
library(dplyr)
library(igraph)
library(ggplot2)
library(quanteda)
#library(tidystm)

lab_corpus_fem_stm <- read_rds("data/lab_corpus_fem_stm.rds")

topic_model_k30 <- read_rds("data/topic_model_k30.rds")

corr_topic_k30 <- read_rds("data/corr_topic_k30.rds")

prep_k30 <- read_rds("data/prep_k30.rds")

prep_df_k30 <- summary(prep_k30)[[3]]

prep_df_k30 <- as.data.frame(do.call(rbind, prep_df_k30))

prep_df_k30$topic <- rep(1:30, each = 2)

prep_df_k30$type <- row.names(prep_df_k30)

prep_df_k30$type <- gsub("\\.[0-9][0-9]", "", prep_df_k30$type)

prep_df_k30$type <- gsub("\\.[0-9]", "", prep_df_k30$type)

prep_df_k30$type <- gsub("\\.$", "", prep_df_k30$type)

prep_df_k30_coeff <- prep_df_k30 %>% filter(type == "short_listTRUE")

vlabels=NULL
layout=NULL

topics <- 1:nrow(corr_topic_k30$posadj)
  
x <- corr_topic_k30$posadj[topics, topics]
  
g <- igraph::graph.adjacency(x, mode="directed", weighted=TRUE, diag=FALSE)
igraph::E(g)$size <- 1
igraph::E(g)$lty <- 2
igraph::E(g)$color <- "black"
igraph::V(g)$label <- topics

plotcord_k30 <- data.frame(layout_with_fr(g))
  
edgelist_k30 <- get.edgelist(g)

#convert to a four column edge data frame with source and destination coordinates
edges_k30 <- data.frame(plotcord_k30[edgelist_k30[,1],],
                        plotcord_k30[edgelist_k30[,2],])
colnames(edges_k30) <- c("X1","Y1","X2","Y2")

plotcord_k30$topic <- as.numeric(row.names(plotcord_k30))
  
plotcord_k30 <- plotcord_k30 %>% left_join(prep_df_k30_coeff)

lab_corpus_fem_stm$meta$eo_id <- docnames(lab_corpus_fem_stm$documents)

topic_dt_k30 <- make.dt(topic_model_k30, lab_corpus_fem_stm$meta)

topic_dt_k30$assigned_topic <- colnames(topic_dt_k30[,2:31])[max.col(topic_dt_k30[,2:31],ties.method="random")]

topic_dt_k30$assigned_topic <- as.factor(topic_dt_k30$assigned_topic)

## Reordering x$assigned_topic
topic_dt_k30$assigned_topic <- factor(topic_dt_k30$assigned_topic, 
                           levels=c("Topic1", "Topic2", "Topic3", 
                                    "Topic4", "Topic5", "Topic6",
                                    "Topic7", "Topic8", "Topic9",
                                    "Topic10", "Topic11", "Topic12", 
                                    "Topic13", "Topic14", "Topic15", 
                                    "Topic16", "Topic17", "Topic18", 
                                    "Topic19", "Topic20", "Topic21", 
                                    "Topic22", "Topic23", "Topic24", 
                                    "Topic25", "Topic26", "Topic27", 
                                    "Topic28", "Topic29", "Topic30"))

topic_dt_k30_2 <- topic_dt_k30 %>% group_by(assigned_topic) %>%
  summarise(count = n()) %>%
  mutate(freq = count/sum(count) )

plotcord_k30$assigned_topic <- paste0("Topic", plotcord_k30$topic)

plotcord_k30 <- plotcord_k30 %>% left_join(topic_dt_k30_2)

p_network_k30 <- ggplot() + 
  geom_segment(aes(x = X1, y = Y1, xend = X2, yend = Y2),
               data = edges_k30, size = 0.5, colour = "grey") +
  geom_point(data = plotcord_k30, 
             aes(X1, X2, colour = Estimate, size = freq)) + 
  geom_text(aes(X1, X2, label = topic), hjust = "center", vjust = "top",
            size = 5, data = plotcord_k30) + 
  scale_colour_viridis(breaks = c(max(plotcord_k30$Estimate),
                                  min(plotcord_k30$Estimate)), 
                       labels = c("More AWS", "More non-AWS"),
                       name = NULL, option = "plasma",
                       end = 0.85, begin = 0.15) + 
  scale_size(guide = "none") + 
  theme_void() + 
  theme(legend.position = "bottom",
    axis.text.x = element_blank(), axis.title.x = element_blank(),
    axis.text.y = element_blank(),axis.title.y = element_blank(),
    axis.ticks = element_blank())

ggsave("p_network_k30.svg", plot = p_network_k30,
         path="plots", device = "svg", width = 20, height = 20, units = "cm")
  
p_network_k30
```

```{r stm-excl-coh-k30, echo=FALSE, fig.cap="\\label{k30-coherence}Coherence of K30 Topic Models"}

library(ggrepel)

sem_test_k30 <- semanticCoherence(topic_model_k30, lab_corpus_fem_stm$documents)

exc_test_k30 <- exclusivity(topic_model_k30)

sem_exc_k30 <- tibble::tibble(topic = 1:30, sem_test_k30, exc_test_k30)

p_sem_exc_k30 <- ggplot(sem_exc_k30, aes(y=exc_test_k30, x = sem_test_k30)) + 
  geom_point() + 
  geom_label_repel(aes(label = topic)) +
  coord_cartesian(xlim = c(-200,0), ylim = c(9.4, 10)) + 
  labs(x="Semantic Coherence", y = "Exclusivity")

  ggsave("p_sem_exc_k30.svg", plot = p_sem_exc_k30,
         path="plots", device = "svg", width = 20, height = 20, units = "cm")
p_sem_exc_k30
```



In all but five topics (gender, immigration, international, children and the environment) the model found p values of < 0.01, and in every topic except the aforemention and "people", p values of < 0.001.

```{r estimate-table-k30, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(knitr)
library(kableExtra)
library(dplyr)

row.names(prep_df_k30) <- NULL
prep_df_k30$type <- gsub("X.Intercept", "Intercept", prep_df_k30$type)
prep_df_k30$type <- gsub("short_listTRUE", "Shortlist", prep_df_k30$type)

prep_df_k30 <- prep_df_k30 %>% rename(
  "p" = "Pr(>|t|)"
)

prep_df_k30$stars <- case_when(prep_df_k30$p < 0.001 ~ "***", 
                               prep_df_k30$p < 0.01 ~ "**",
                               prep_df_k30$p < 0.05 ~ "*", 
                               TRUE ~ "")

prep_df_k30_2 <- prep_df_k30 %>% select(type, Estimate,
                                        `Std. Error`, `t value`, p, stars) %>%
  mutate(p = pixiedust::pval_string(p,  digits = 4))

kable(prep_df_k30_2, booktabs = TRUE, longtable = TRUE, 
      caption = "Topic Estimates",
      col.names = c("", "Estimate", "Standard Error",
                    "t value", "Pr(>|t|)", ""),
      align = c("l","r","r","r","r", "l")) %>%
  kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE ) %>%
   group_rows(index = c("Topic 1 -- Bills" = 2,
                        "Topic 2 -- Consultations" = 2,
                        "Topic 3 -- Members" = 2,
                        "Topic 4 -- Gender" = 2,
                        "Topic 5 -- Civic society" = 2,
                        "Topic 6 -- International" = 2,
                        "Topic 7 -- Disability" = 2,
                        "Topic 8 -- Rural Issues" = 2,
                        "Topic 9 -- Immigration" = 2,
                        "Topic 10 -- Health Care" = 2,
                        "Topic 11 -- Parties" = 2,
                        "Topic 12 -- Constituencies" = 2,
                        "Topic 13 -- Security" = 2,
                        "Topic 14 -- Investment" = 2,
                        "Topic 15 -- Youth" = 2,
                        "Topic 16 -- Energy" = 2,
                        "Topic 17 -- Local authorities" = 2,
                        "Topic 18 -- People" = 2,
                        "Topic 19 -- Education" = 2,
                        "Topic 20 -- Transport" = 2,
                        "Topic 21 -- Housing" = 2,
                        "Topic 22 -- Tax" = 2,
                        "Topic 23 -- Police" = 2,
                        "Topic 24 -- Media" = 2,
                        "Topic 25 -- Families" = 2,
                        "Topic 26 -- Environment" = 2,
                        "Topic 27 -- Ministers" = 2,
                        "Topic 28 -- Regions" = 2,
                        "Topic 29 -- Pensions" = 2,
                        "Topic 30 -- Technology" = 2))
```


```{r topic-diversity-k30, echo=FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
#head(topic_dt_k30)

#summary(topic_dt_k30$mnis_id)

topic_dt_k30_div <- topic_dt_k30 %>% 
  mutate(assigned_topic = gsub("Topic", "Topic ", assigned_topic)) %>% 
  group_by(assigned_topic, mnis_id) %>%
  tally() %>% ungroup() %>% 
  group_by(assigned_topic)  %>%
  summarise(distinct_n5 = sum(n >= 5),
            distinct = n()) %>%
  select(assigned_topic, distinct, distinct_n5) %>%
   mutate(assigned_topic = recode(assigned_topic,
                                  "Topic 1" = "Bills",
                                  "Topic 2" = "Consultations",
                                  "Topic 3" = "Members",
                                  "Topic 4" = "Gender",
                                  "Topic 5" = "Civic society",
                                  "Topic 6" = "International",
                                  "Topic 7" = "Disability",
                                  "Topic 8" = "Rural Issues",
                                  "Topic 9" = "Immigration",
                                  "Topic 10" = "Health Care",
                                  "Topic 11" = "Parties",
                                  "Topic 12" = "Constituencies",
                                  "Topic 13" = "Security",
                                  "Topic 14" = "Investment",
                                  "Topic 15" = "Youth",
                                  "Topic 16" = "Energy",
                                  "Topic 17" = "Local authorities",
                                  "Topic 18" = "People",
                                  "Topic 19" = "Education",
                                  "Topic 20" = "Transport",
                                  "Topic 21" = "Housing",
                                  "Topic 22" = "Tax",
                                  "Topic 23" = "Police",
                                  "Topic 24" = "Media",
                                  "Topic 25" = "Families",
                                  "Topic 26" = "Environment",
                                  "Topic 27" = "Ministers",
                                  "Topic 28" = "Regions",
                                  "Topic 29" = "Pensions",
                                  "Topic 30" = "Technology"))

topic_dt_k30_div$prop <- topic_dt_k30_div$distinct_n5/topic_dt_k30_div$distinct

kable(topic_dt_k30_div[1:3],  booktabs = TRUE, longtable = TRUE, 
      caption = "Distribution of Topics Among Female Labour MPs -- K30",
      col.names = c("Topic", "One or more speeches", "Five or more speeches"),
      align = c("l","r","r")) %>%
    kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE )
```

There is no topic that every single female Labour MP has discussed at least once. The most widely used is the topic "People", which out of `r sum(lab_nums$distinct[lab_nums$gender=="Female"])` female Labour MPs in the dataset, `r scales::percent(topic_dt_k30_div$distinct[topic_dt_k30_div$assigned_topic=="People"])`  made at least one speech in that topic. `r scales::percent(topic_dt_k30_div$prop[topic_dt_k30_div$assigned_topic=="People"])` of those MPs made five or more speeches about "People".


```{r topic-dt-man-creation-k30, include=FALSE}
library(scales)
library(tidyr)

topic_model_man_k30 <- read_rds("data/topic_model_man_k30.rds")
new_man_k30 <- read_rds("data/new_man_k30.rds")

new_man_k30$meta$eo_id <- docnames(new_man_k30$documents)

topic_man_dt_k30 <- make.dt(topic_model_man_k30, new_man_k30$meta)

topic_man_dt_k30$assigned_topic <- colnames(topic_man_dt_k30[,2:31])[max.col(topic_man_dt_k30[,2:31],ties.method="random")]

topic_man_dt_k30$assigned_topic <- as.factor(topic_man_dt_k30$assigned_topic)

## Reordering x$assigned_topic
topic_man_dt_k30$assigned_topic <- factor(topic_man_dt_k30$assigned_topic, 
                           levels=c("Topic1", "Topic2", "Topic3", 
                                    "Topic4", "Topic5", "Topic6",
                                    "Topic7", "Topic8", "Topic9",
                                    "Topic10", "Topic11", "Topic12", 
                                    "Topic13", "Topic14", "Topic15", 
                                    "Topic16", "Topic17", "Topic18", 
                                    "Topic19", "Topic20", "Topic21", 
                                    "Topic22", "Topic23", "Topic24", 
                                    "Topic25", "Topic26", "Topic27", 
                                    "Topic28", "Topic29", "Topic30"))

topic_man_dt_k30_2 <- topic_man_dt_k30 %>% group_by(assigned_topic) %>%
  summarise(man_count = n()) %>%
  mutate(man_freq = man_count/sum(man_count, na.rm = TRUE),
         assigned_topic = gsub("Topic", "Topic ", assigned_topic))

```

```{r topic-dt3-creation-k30, include=FALSE}
topic_dt_k30_3 <- topic_dt_k30 %>% group_by(assigned_topic, short_list) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  spread(key = "short_list", value = "count") %>%
  rename("AWS" = "TRUE", "non_AWS" = "FALSE") %>%
  mutate(AWS_freq = AWS/sum(AWS, na.rm = TRUE),
         non_AWS_freq = non_AWS/sum(non_AWS, na.rm = TRUE),
         assigned_topic = gsub("Topic", "Topic ", assigned_topic)) %>%
  select(assigned_topic, AWS, AWS_freq, non_AWS, non_AWS_freq) %>%
  left_join(topic_man_dt_k30_2)

topic_dt_k30_4 <- topic_dt_k30_3 %>% 
    mutate(AWS_freq = paste0(round((AWS_freq*100),2), "%"),
          non_AWS_freq = paste0(round((non_AWS_freq*100),2), "%"),
          AWS = formatC(AWS, big.mark = ","),
          non_AWS = formatC(non_AWS, big.mark = ","),
          man_freq = paste0(round((man_freq*100),2), "%"),
          man_count = formatC(man_count, big.mark = ","),
        assigned_topic = recode(assigned_topic,
                                "Topic 1" = "Bills",
                                "Topic 2" = "Consultations",
                                "Topic 3" = "Members",
                                "Topic 4" = "Gender",
                                "Topic 5" = "Civic society",
                                 "Topic 6" = "International",
                                 "Topic 7" = "Disability",
                                 "Topic 8" = "Rural Issues",
                                "Topic 9" = "Immigration",
                                "Topic 10" = "Health Care",
                                "Topic 11" = "Parties",
                                "Topic 12" = "Constituencies",
                                "Topic 13" = "Security",
                                "Topic 14" = "Investment",
                                "Topic 15" = "Youth",
                                "Topic 16" = "Energy",
                                 "Topic 17" = "Local authorities",
                                 "Topic 18" = "People",
                                 "Topic 19" = "Education",
                                 "Topic 20" = "Transport",
                                 "Topic 21" = "Housing",
                                 "Topic 22" = "Tax",
                                 "Topic 23" = "Police",
                                 "Topic 24" = "Media",
                                 "Topic 25" = "Families",
                                "Topic 26" = "Environment",
                                "Topic 27" = "Ministers",
                                "Topic 28" = "Regions",
                                "Topic 29" = "Pensions",
                                "Topic 30" = "Technology")
          )

```

```{r topic-summary-table-k30, echo=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)

kable(topic_dt_k30_4,  booktabs = TRUE, longtable = TRUE, 
      caption = "Count and Distribution of Topics -- K30",
      col.names = c("Topic Number", "AWS Speeches", "Percent of AWS Speeches",
                    "Non-AWS Speeches", "Percent of non-AWS Speeches",
                    "Male MP Speeches", "Percent of Male MP Speeches"),
      align = c("l","r","r","r","r","r","r")) %>%
    kable_styling(latex_options = c("HOLD_position",  "repeat_header",
                                    "striped"), full_width = TRUE )
```


```{r k30-topic-pyramid, echo=FALSE, fig.height=9, fig.cap="\\label{k30-topic-pyramid-plot}K30 Pyramid Chart"}

topic_dt_k30_3$prop <- topic_dt_k30_3$AWS_freq/topic_dt_k30_3$non_AWS_freq

topic_dt_k30_5 <- topic_dt_k30_3 %>% 
  select(assigned_topic, AWS_freq, non_AWS_freq) %>%
  gather("aws_status", "perc", -assigned_topic) %>%
  mutate(assigned_topic = factor(assigned_topic, 
                                 levels=c("Topic 1", "Topic 2", "Topic 3",
                                          "Topic 4", "Topic 5", "Topic 6",
                                          "Topic 7", "Topic 8", "Topic 9",
                                          "Topic 10", "Topic 11", "Topic 12", 
                                          "Topic 13", "Topic 14", "Topic 15", 
                                          "Topic 16", "Topic 17", "Topic 18", 
                                          "Topic 19", "Topic 20", "Topic 21", 
                                          "Topic 22", "Topic 23", "Topic 24", 
                                          "Topic 25", "Topic 26", "Topic 27", 
                                          "Topic 28", "Topic 29", "Topic 30")),
          assigned_topic = recode(assigned_topic,
         "Topic 1" = "Bills",
                                "Topic 2" = "Consultations",
                                "Topic 3" = "Members",
                                "Topic 4" = "Gender",
                                "Topic 5" = "Civic society",
                                 "Topic 6" = "International",
                                 "Topic 7" = "Disability",
                                 "Topic 8" = "Rural Issues",
                                "Topic 9" = "Immigration",
                                "Topic 10" = "Health Care",
                                "Topic 11" = "Parties",
                                "Topic 12" = "Constituencies",
                                "Topic 13" = "Security",
                                "Topic 14" = "Investment",
                                "Topic 15" = "Youth",
                                "Topic 16" = "Energy",
                                 "Topic 17" = "Local authorities",
                                 "Topic 18" = "People",
                                 "Topic 19" = "Education",
                                 "Topic 20" = "Transport",
                                 "Topic 21" = "Housing",
                                 "Topic 22" = "Tax",
                                 "Topic 23" = "Police",
                                 "Topic 24" = "Media",
                                 "Topic 25" = "Families",
                                "Topic 26" = "Environment",
                                "Topic 27" = "Ministers",
                                "Topic 28" = "Regions",
                                "Topic 29" = "Pensions",
                                "Topic 30" = "Technology")
         )

topic_dt_k30_5$perc[is.na(topic_dt_k30_5$perc)] <- 0

p_k30_pyramid <- ggplot(data = topic_dt_k30_5, 
                        aes(x = assigned_topic, y = perc, fill = aws_status)) +
  geom_bar(data = filter(topic_dt_k30_5, aws_status == "non_AWS_freq"),
           stat = "identity" ) + 
  geom_bar(data = filter(topic_dt_k30_5, aws_status == "AWS_freq"),
           stat = "identity", aes(y = -perc)) + 
  geom_bar(data = filter(topic_dt_k30_5, aws_status == "AWS_freq"),
           stat = "identity", aes(color = aws_status),
           alpha = 0, color = "#641A80") + 
  geom_bar(data = filter(topic_dt_k30_5, aws_status == "non_AWS_freq"),
           stat = "identity", aes(color = aws_status, y = -perc),
           alpha = 0, color = "#F76F5C") + 
  scale_y_continuous(breaks = seq(-0.125, 0.125, 0.025), 
                     labels = paste0(
                       as.character(c(seq(12.5, 0, -2.5),
                                      seq(2.5, 12.5, 2.5))), "%")) + 
  coord_flip(ylim = c(-0.125, 0.125)) + 
  scale_fill_viridis_d(labels = c("AWS", "non-AWS"),
                       begin = 0.3, end = 0.7, option = "magma", name = "") + 
  labs(x = "Topic", y = "Percentage of Speeches") + 
  theme(legend.position = "bottom")

ggsave("p_k30_pyramid.svg", plot = p_k30_pyramid,
       path="plots", device = "svg", width = 20, height = 20, units = "cm")

p_k30_pyramid
```


```{r k30-topic-bar, echo=FALSE, fig.cap="\\label{k30-topic-bar-plot}K30 Bar Chart"}
p_k30_bar <- ggplot(data = topic_dt_k30_5,
                    aes(x = assigned_topic, y = perc, fill = aws_status)) +
  geom_bar(stat = "identity", position = "dodge") + 
  scale_y_continuous(breaks = c(0, 0.025, 0.05, 0.075, 0.1, 0.125),
                     labels = scales::percent) + 
  scale_fill_viridis_d(labels = c("AWS", "non-AWS"),
                       begin = 0.3, end = 0.7, option = "magma", name = "") + 
  labs(x = "Topic", y = "Percentage of Speeches") + 
  theme(legend.position = "bottom", 
        axis.text.x = element_text(angle = 90, hjust = 1))

ggsave("p_k30_bar.svg", plot = p_k30_bar,
       path="plots", device = "svg", width = 20, height = 20, units = "cm")

p_k30_bar
```


```{r top-n-topics-k30, eval=FALSE, include=FALSE}

aws_top10 <- top_n(topic_dt_k30_3, 10, AWS)
non_aws_top10 <- top_n(topic_dt_k30_3, 10, non_AWS)

cor.test(topic_dt_k30_3$non_AWS_freq, topic_dt_k30_3$man_freq, na.rm = TRUE)

topic_dt_k30_5 <- topic_dt_k30_3 %>% select(assigned_topic, AWS_freq, non_AWS_freq, man_freq)

df <- table(topic_dt_k30_5)

# run test
#mantelhaen.test(topic_dt_k30_3$assigned_topic)

```

```{r stm-topic-words-k30, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
library(tidyr)
topic_words <- labelTopics(topic_model_k30, n = 20, frexweight = 0.5)

topic_words_highest <- tibble::as_tibble(topic_words[[1]])

topic_words_highest <- topic_words_highest %>% unite(V1:V10, sep = ", ") %>%
  rename("highest" = "V1:V10")

topic_words_highest$topic <- paste0("Topic ", row.names(topic_words_highest))

topic_words_frex <- tibble::as_tibble(topic_words[[2]])

topic_words_frex <- topic_words_frex %>% unite(V1:V10, sep = ", ") %>%
  rename("FREX" = "V1:V10")

topic_words_frex$topic <- paste0("Topic ", row.names(topic_words_frex))

topic_words2 <- topic_words_highest %>% left_join(topic_words_frex) %>% 
  select(topic, everything())
```

AWS are -- proportionally -- more likely than non-AWS MPs to discuss Topics 29 (parliament), 7 (disability) and 24 (media). They are proportionally less likely to mention Topics 15 (justice), 2 (consultations) and 9 (disease). See Figure \ref{k30-topic-proportion} for more details. Perhaps surprisingly, AWS MPs are slightly less likely to mention gender issues (Topic 3), although the difference is not statistically significant (see [the appendix][Full topic model estimate summary - K30] for details).

```{r k30-topic-proportion, echo=FALSE, fig.cap="\\label{k30-topic-proportion}K30 Topic Proportions"}
topic_dt_k30_3$prop <- topic_dt_k30_3$AWS_freq/topic_dt_k30_3$non_AWS_freq

topic_dt_k30_6 <- topic_dt_k30_3 %>% 
  select(assigned_topic, prop) %>%
  mutate(assigned_topic = factor(assigned_topic, 
                                 levels=c("Topic 1", "Topic 2", "Topic 3",
                                          "Topic 4", "Topic 5", "Topic 6",
                                          "Topic 7", "Topic 8", "Topic 9",
                                          "Topic 10", "Topic 11", "Topic 12", 
                                          "Topic 13", "Topic 14", "Topic 15", 
                                          "Topic 16", "Topic 17", "Topic 18", 
                                          "Topic 19", "Topic 20", "Topic 21", 
                                          "Topic 22", "Topic 23", "Topic 24", 
                                          "Topic 25", "Topic 26", "Topic 27", 
                                          "Topic 28", "Topic 29", "Topic 30")),
          assigned_topic = recode(assigned_topic,
                                  "Topic 1" = "Bills",
                                  "Topic 2" = "Consultations",
                                  "Topic 3" = "Members",
                                  "Topic 4" = "Gender",
                                  "Topic 5" = "Civic society",
                                  "Topic 6" = "International",
                                  "Topic 7" = "Disability",
                                  "Topic 8" = "Rural Issues",
                                  "Topic 9" = "Immigration",
                                  "Topic 10" = "Health Care",
                                  "Topic 11" = "Parties",
                                  "Topic 12" = "Constituencies",
                                  "Topic 13" = "Security",
                                  "Topic 14" = "Investment",
                                  "Topic 15" = "Youth",
                                  "Topic 16" = "Energy",
                                  "Topic 17" = "Local authorities",
                                  "Topic 18" = "People",
                                  "Topic 19" = "Education",
                                  "Topic 20" = "Transport",
                                  "Topic 21" = "Housing",
                                  "Topic 22" = "Tax",
                                  "Topic 23" = "Police",
                                  "Topic 24" = "Media",
                                  "Topic 25" = "Families",
                                  "Topic 26" = "Environment",
                                  "Topic 27" = "Ministers",
                                  "Topic 28" = "Regions",
                                  "Topic 29" = "Pensions",
                                  "Topic 30" = "Technology"),
         assigned_topic = as.character(assigned_topic),
         prop = if_else(prop < 1, 
                        (1 - prop) * -1, 
                        prop - 1)) %>%
  arrange(prop)

topic_dt_k30_6$assigned_topic <- reorder(topic_dt_k30_6$assigned_topic, topic_dt_k30_6$prop)

p_k30_prop <- ggplot(data = topic_dt_k30_6, 
                     aes(x = assigned_topic,
                         y = prop, fill = prop)) +
  geom_bar(stat = "identity") + 
  scale_y_continuous() + 
  scale_fill_viridis_c(name = "") + 
  coord_flip() + 
  labs(x = "Topic", 
       y = "Proportion of speeches made by AWS MPs (right side)\nrelative to non-AWS MPs (left side)") + 
  theme(legend.position = "bottom")

ggsave("p_k30_prop.svg", plot = p_k30_prop,
       path="plots", device = "svg", width = 20, height = 20, units = "cm")

p_k30_prop
```

```{r eval=FALSE, include=FALSE}

#lab_corpus_fem$documents$texts

lab_corpus_fem2 <- lab_corpus_fem %>% corpus_subset(docnames(lab_corpus_fem) %in% docnames(lab_corpus_fem_stm$documents))

# lab_corpus_fem_stm$meta$eo_id <- docnames(lab_corpus_fem_stm$documents)

## AWS
thought29 <- findThoughts(topic_model_k30, texts=lab_corpus_fem2$documents$texts,
                       topics=29, n=3)

thought7 <- findThoughts(topic_model_k30, texts=lab_corpus_fem2$documents$texts,
                       topics=7, n=3)

thought24 <- findThoughts(topic_model_k30, texts=lab_corpus_fem2$documents$texts,
                       topics=24, n=3)

plotQuote(thought29, width = 30, main = "Topic 3")
```


#### Word Occurences

The table below shows the twenty most common words in each topic, and the twenty words with the highest FREX score, a measure that uses a harmonic mean of word exclusivity and topic coherence  [@airoldi2016].

```{r topic-words-table-k30, echo=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)

kable(topic_words2, booktabs = TRUE, longtable = TRUE, 
      col.names = c("Topic Number", "Top Ten Words", "Top Ten FREX"),
      caption = "Words in Topic - K30") %>%
    kable_styling(latex_options = c("HOLD_position", "repeat_header",
                                    "striped"), full_width = TRUE ) %>% 
  column_spec(2:3, width = "6cm")
```

```{r tidy-text-testing-k30, eval=FALSE, include=FALSE}
library(tidytext)
test3 <- tidytext::tidy(topic_model_k30, matrix = "gamma",
                        document_names = rownames(topic_model_k30))


test4 <- test3  %>%
  group_by(document) %>%
  top_n(1, gamma) %>%
  ungroup() %>%
  arrange(document, -gamma)

test5 <- tidytext::tidy(topic_model_k30, matrix = "beta")

test6 <- test5  %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

head(test6)
```


### Full topic model summary - K30

```{r topic-model-k30-summary, echo=FALSE, message=FALSE}
summary(topic_model_k30)
```

### Full topic model estimate summary - K30

```{r topic-model2-k30-est-summary, echo=FALSE, message=FALSE}
summary(prep_k30)
```

