---
title: "All Women Shortlists Scratchpad"
output: html_notebook
bibliography: women.bib
link-citations: true
editor_options: 
  chunk_output_type: inline
---


```{r pro-bigram-plots, eval=FALSE, include=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(magrittr)

pro_bigram <- read_rds("pro_bigram.rds")

docvars(pro_bigram, "year") <- lubridate::year(docvars(pro_bigram, "speech_date"))

pro_dfm <- dfm(pro_bigram, verbose=TRUE, groups = c("short_list", "year")) %>%
  dfm_trim(min_termfreq = 25)

#x <- textstat_frequency(pro_dfm, n = NULL, groups = c("short_list", "year"))

pro_dfm_df <- tibble::as.tibble(as.data.frame(pro_dfm))

pro_dfm_df2 <- pro_dfm_df %>% 
  separate("document", into = c("short_list", "year"), remove = FALSE) %>%
  select(short_list, year, everything()) %>% 
  group_by(short_list, year) %>% 
  mutate_at(vars(i_hope:our_amendments), as.numeric, na.rm=TRUE) %>% 
  mutate(total = sum(i_hope:our_amendments), 
         cons_total = sum(my_constituents, my_constituency,
                          my_constituent, na.rm=TRUE),
         cons_perc = cons_total/total)

pro_dfm_df2$year <- factor(pro_dfm_df2$year)

my_cons_plot <- ggplot(pro_dfm_df2, 
                       aes(x=year, y = cons_perc,
                           group = short_list, colour = short_list)) + 
  geom_point()

my_cons_plot
```


```{r tidy-text-testing, eval=FALSE, include=FALSE}
library(tidytext)
test3 <- tidytext::tidy(topic_model2, matrix = "gamma",
                        document_names = rownames(topic_model2))


test4 <- test3  %>%
  group_by(document) %>%
  top_n(1, gamma) %>%
  ungroup() %>%
  arrange(document, -gamma)

test5 <- tidytext::tidy(topic_model2, matrix = "beta")

test6 <- test5  %>%
  group_by(topic) %>%
  top_n(5, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

head(test6)
```




```{r lab-desc-stats, eval=FALSE, include=FALSE}
elections <- as.POSIXct(c("1997-05-01", "2001-06-07", "2005-05-05", 
               "2010-05-06", "2015-05-07", "2017-06-07"), tz = "UTC")

labour_intakes <- lab_speech %>% 
  filter(house_start_date %in% elections) %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(total=n()) 

labour_intakes_women <- lab_speech %>% 
  filter(house_start_date %in% elections, gender=="Female") %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(women=n()) 

labour_intakes <- labour_intakes %>% left_join(labour_intakes_women)
labour_intakes$perc_women <- (labour_intakes$women/labour_intakes$total)*100

```






Existing work on this topic has either compared women and men, or tracked changes in a single woman [@jones2016] or group of women. 


### Extracing post-1997 Labour speeches

```{r}
library(readr)
library(dplyr)
library(quanteda)
library(readxl)
library(lubridate)

all_speech <- read_rds("senti_df2.rds")

## Binned into quarters of a year
all_speech$y_since_start <- round(time_length(all_speech$speech_date -
                                          as.Date(all_speech$house_start_date),
                                        unit = "years")* 4)/4

lab_speech <- filter(all_speech, party_group=="Labour", 
      speech_date >= "1997-05-01", speech_date < "2017-06-08", word_count > 0)

rm(all_speech)

all_women97_15 <- read_excel("list-of-mps.xlsx")

lab_speech$short_list <- lab_speech$mnis_id %in% all_women97_15$mnis

#library(stringi)
## Pattern replacing part 1
# (try to do this vectorised style?)
# lab_speech$speech <- stri_replace_all_regex(lab_speech$speech, '(?:\\srt\\s|\\srt.\\s|\\sright\\s){1}(?:hon\\s|hon.\\s|honourable\\s){1}',
#                                             " Right Honourable ")
# 
# lab_speech$speech <- stri_replace_all_regex(lab_speech$speech, 
#                                             '(?:\\shon\\s|\\shon.\\s){1}', 
#                                             " Honourable ")
# 
# ### This is next bit doesn't work, not sure why that is
# lab_speech$speech <- stri_replace_all_regex(lab_speech$speech,   '(?:(?:right\\s){0,1}(?:honourable\\s|noble\\s){1}(?:(?:and\\s)|(?:lord\\s)|(?:honourable\\s)|(?:learned\\s)|(?:gallant\\s)|(?:noble\\s)|(?:respected\\s)|(?:reverend\\s)){0,4}(?:the\\s){0,1}(?:(?:lord(?:s){0,1})|(?:justice(?:s){0,1}\\b)|(?:gentle\\sm[ea]n(?:t){0,1})|(?:gentlem[ea]n(?:t){0,1})|(?:friend(?:s){0,1}\\b)|(?:member(?:s){0,1}\\b)|(?:lad(?:y|(?:ies)){1})){1})',"formal_title")
# 
# test <- gsub('(?:(?:right\\s){0,1}(?:honourable\\s|noble\\s){1}(?:(?:and\\s)|(?:lord\\s)|(?:honourable\\s)|(?:learned\\s)|(?:gallant\\s)|(?:noble\\s)|(?:respected\\s)|(?:reverend\\s)){0,4}(?:the\\s){0,1}(?:(?:lord(?:s){0,1})|(?:justice(?:s){0,1}\\b)|(?:gentle\\sm[ea]n(?:t){0,1})|(?:gentlem[ea]n(?:t){0,1})|(?:friend(?:s){0,1}\\b)|(?:member(?:s){0,1}\\b)|(?:lad(?:y|(?:ies)){1})){1})',"formal_title", lab_speech$speech)

lab_corpus <- corpus(lab_speech, docid_field = "eo_id", text_field = "speech")
```




# Descriptive Statistics

```{r eval=FALSE, include=FALSE}
elections <- as.POSIXct(c("1997-05-01", "2001-06-07", "2005-05-05", 
               "2010-05-06", "2015-05-07", "2017-06-07"), tz = "UTC")

labour_intakes <- lab_speech %>% 
  filter(house_start_date %in% elections) %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(total=n()) 

labour_intakes_women <- lab_speech %>% 
  filter(house_start_date %in% elections, gender=="Female") %>% 
  group_by(house_start_date, mnis_id) %>% 
  summarise() %>% 
  group_by(house_start_date) %>% 
  summarise(women=n()) 

labour_intakes <- labour_intakes %>%  left_join(labour_intakes_women)
labour_intakes$perc_women <- (labour_intakes$women/labour_intakes$total)*100

```


- Statistics on the gender of Labour MPs in each general election:

| General Election | Total MPs | Total Labour MPs | Total Female Labour MPs | Newly elected MPs | Intake Women | Percentage Intake Women | Intake Shortlist | Nominated Shortlist |
|---|---|---|---|---|---|---|---|---|---|
| 1997 | 659 | 418 | 101 | 177 | 64 |36% | 35 | 38 |
| 2001 | 659 | 412 | 95 | 38 | 4 | 11% | 0 | 0 |
| 2005 | 646 | 355 | 98 | 40 | 26 | 65% | 23 | 30 |
| 2010 | 650 | 258 | 81 | 64 | 32 | 50% | 28 | 63 |
| 2015 | 650 | 232 | 99 | 49 | 31 | 63% | 31 | 77 |

Stats from [@kelly2016] and [@audickas2017]. All women shortlists were not used for the 2001 General Election




### Load women speeches

All women shortlists are from house of commons library [@kelly2016]

Hypothesis:
- Women selected through all women shortlists use more "feminine" language -- pronouns, particular personal pronouns, passive voice, hedges, etc -- than women selected in open selections.

Plan of attack:

- Use one of the `cleanNLP` packages to get everything running.
- Group by election, party, only include women elected after 1997?
- Check Jones2016 for more info
- Group by cohort and intake



### Women vs Men

```{r}
#remotes::install_github("kbenoit/quanteda.dictionaries")
library(quanteda.dictionaries)
library(purrr)
library(tidyr)

liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic",
       format = "LIWC")

lab_liwc <- liwcalike(lab_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

lab_liwc[["Sixltr"]] <- sapply(quanteda::tokens(texts(lab_corpus), remove_hyphens = TRUE), function(y) sum(stringi::stri_length(y) > 6)) / lab_liwc[["WC"]] * 100

#write_rds(lab_liwc, "lab_liwc.rds")

lab_liwc <- read_rds("lab_liwc.rds")

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc)[4:91]

lab_liwc_men_women_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc %>%
   group_by(gender) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

#tibble::glimpse(lab_liwc_men_women_mean)

lab_liwc_men_women_tidy_mean <- gather(lab_liwc_men_women_mean, 
          "attribute", "weighted_mean",
          -gender, -WC) 

lab_liwc_men_women_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc %>%
   group_by(gender) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_men_women_tidy_sd <- gather(lab_liwc_men_women_sd, "attribute",
          "sd", -gender, -WC) 

## Joining together the SD and Means to get CIs

## Calculate Cohen's D in here somehow?
lab_liwc_men_women2 <- left_join(lab_liwc_men_women_tidy_mean, 
         lab_liwc_men_women_tidy_sd) %>% 
 left_join(lab_liwc %>% 
    group_by(gender) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

rm(lab_liwc_men_women_tidy_sd, lab_liwc_men_women_tidy_mean)

fem_mac <- c("pronoun", "i", "verb", "auxverb", "social", "posemo", 
             "negemo", "cogmech", "tentat", "Sixltr", "we", 
             "article", "prep", "anger", "swear")

lab_liwc_men_women2_subset <- lab_liwc_men_women2 %>%
  filter(attribute %in% fem_mac)

#devtools::install_github("tidyverse/ggplot2")
library(ggplot2)

p_men_women <- ggplot(aes(y = weighted_mean, x = gender),
                      data = lab_liwc_men_women2_subset) + 
  geom_col() + 
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci),
                width = 0.2) +
  facet_wrap(~attribute)

p_men_women

### Maybe do something different instead of this?

lmtest <- lm(pronoun ~ gender, data = lab_liwc)

library(effsize)

cohen.d.default(lab_liwc, lab_liwc$gender, noncentral = TRUE)


## Is this the right thing to be doing here?
test <- lapply((lab_liwc)[4:79], cohen.d, lab_liwc$gender, pooled = TRUE,
       na.rm = TRUE, noncentral = TRUE)

```




### Shortlists vs Non-Shortlists

```{r}
#liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic", format = "LIWC")

lab_speech_women <- filter(lab_speech, gender=="Female", 
                           speech_date >= "1997-05-01", 
                           speech_date < "2017-06-08", word_count > 0)

lab_women_corpus <- corpus(lab_speech_women, docid_field = "eo_id",
                           text_field = "speech")

lab_liwc_women <- liwcalike(lab_women_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc_women)[4:91]

lab_liwc_women_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_women %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

tibble::glimpse(lab_liwc_women_mean)

lab_liwc_women_tidy_mean <- gather(lab_liwc_women_mean, "attribute",
                                   "weighted_mean", -short_list, -gender, -WC) 


lab_liwc_women_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc_women %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_women_tidy_sd <- gather(lab_liwc_women_sd, "attribute",
                                 "sd", -short_list, -gender, -WC) 

## Joining together the SD and Means to get CIs
lab_liwc_women2 <- left_join(lab_liwc_women_tidy_mean,
                             lab_liwc_women_tidy_sd) %>% 
 left_join(lab_liwc_women %>% 
    group_by(gender, short_list) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)
```



### Shortlists vs Non-Shortlists vs Men

```{r}
liwc15_dict <- dictionary(file = "dict/LIWC2015_English_Flat.dic", format = "LIWC")

lab_liwc <- liwcalike(lab_corpus, 
      dictionary = liwc15_dict, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

## Group by gender, short_lsit, see what's up
cols <- names(lab_liwc)[4:91]

lab_liwc_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

tibble::glimpse(lab_liwc_mean)

lab_liwc_tidy_mean <- gather(lab_liwc_mean, "attribute", "weighted_mean",
        -short_list, -gender, -WC) 


lab_liwc_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_tidy_sd <- gather(lab_liwc_sd, "attribute", "sd", -short_list,
        -gender, -WC) 

## Joining together the SD and Means to get CIs
lab_liwc2 <- left_join(lab_liwc_tidy_mean, lab_liwc_tidy_sd) %>% 
 left_join(lab_liwc %>% 
    group_by(gender, short_list) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
   lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
   upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

```

#### Masculine and Feminine thingys
Feminine: 
  - pronoun
  - i 
  - verb
  - auxverb 
  - social 
  - posemo 
  - negemo 
  - cogmech
  - tentat
  
Masculine:
  - Sixltr
  - we
  - article 
  - preps 
  - anger
  - swear

### Do the same thing as above, but this time only with MPs elected in 1997 or onwards



### Tokenising 

```{r}
### Need to strip out all that crap refering to constituencies and decorum currently stored in perl script
lab_tokens <- tokens(lab_corpus, what = "word", include_docvars = TRUE,
      remove_punct = TRUE)### Do something to only include the short_list and gender docvars

lab_dfm <- dfm(lab_tokens, remove = stopwords("english"), verbose = TRUE)

lab_freq <- textstat_frequency(lab_dfm, groups = c("short_list", "gender"))

lab_keyness <- textstat_keyness(lab_dfm) ## this isn't working the way I want it to. Going off the wrong docvar?

```



### Experiment in plotting

```{r}

lab_liwc_lg_mean_no_min <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_lg %>%
   group_by(gender, short_list) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_lg_tidy_mean_no_min <- gather(lab_liwc_lg_mean_no_min, "attribute", 
         "weighted_mean", -short_list, -gender, -WC) 


p0 <- ggplot(aes(y = weighted_mean, x = attribute,
     group = interaction(gender, short_list)),
    data=filter(lab_liwc_lg_tidy_mean_no_min,
       attribute != "WPS", attribute != "AllPunc")) + 
 geom_col(position = "dodge", aes(fill=gender))

p0

```






### liwc with LG dictionary

Using [@benoit2018] with `liwcalike` function from the `quanteda.dictionaries` package

```{r}
#lab_dfm <- dfm(lab_corpus, groups = c("short_list", "gender"))

#lab_dist <- textstat_dist(lab_dfm, selection = NULL, margin = "features",
# method = "euclidean", upper = FALSE, diag = FALSE, p = 2)

## Interesting dictionary
lab_liwc_lg <- liwcalike(lab_corpus, 
      dictionary = data_dictionary_LaverGarry, 
      verbose = TRUE) %>%
 left_join(lab_speech, by = c("docname" = "eo_id"))

cols <- names(lab_liwc_lg)[4:37]

lab_liwc_lg_mean <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(weighted.mean(., WC))),
  ~ lab_liwc_lg %>%
   group_by(gender, short_list, ministry) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

tibble::glimpse(lab_liwc_lg_mean)

lab_liwc_lg_tidy_mean <- gather(lab_liwc_lg_mean, "attribute", "weighted_mean", -short_list,
        -gender, -ministry, -WC) 


lab_liwc_lg_sd <- list(c("WC"), cols) %>%
 map2(lst(mean=mean, funs(sd(., na.rm=TRUE))),
  ~ lab_liwc_lg %>%
   group_by(gender, short_list, ministry) %>%
   summarise_at(.x, .y)) %>%
 reduce(inner_join)

lab_liwc_lg_tidy_sd <- gather(lab_liwc_lg_sd, "attribute", "sd", -short_list,
        -gender, -ministry, -WC) 

## Joining together the SD and Means to get CIs
lab_liwc_lg2 <- left_join(lab_liwc_lg_tidy_mean, lab_liwc_lg_tidy_sd) %>% 
 left_join(lab_liwc_lg %>% 
 group_by(gender, short_list, ministry) %>% summarise(n=n())) %>%
 mutate(se = sd / sqrt(n),
  lower_ci = weighted_mean - qt(1 - (0.05 / 2), n - 1) * se,
 upper_ci = weighted_mean + qt(1 - (0.05 / 2), n - 1) * se)

library(ggplot2)

lab_liwc_lg2$attribute <- as.factor(lab_liwc_lg2$attribute)

## Test Case
p1 <- ggplot(aes(y = weighted_mean, x = ministry,
     group = interaction(gender, short_list)), 
    data = filter(lab_liwc_lg2, attribute == "values.conservative")) + 
 geom_line(aes(colour = gender, linetype=short_list)) + 
 geom_ribbon(aes(ymin=lower_ci,ymax=upper_ci),alpha=0.3)

p1

### ID the areas of possible difference

fem <- filter(lab_liwc_lg2, gender=="Female")


```




### Spacy

```{r}
lab_speech$year <- as.factor(lab_speech$year)

split_data <- split(lab_speech, lab_speech$year) ### Splitting data variable

all_names <- names(split_data)

for (this_name in all_names) {
  df <- corpus(split_data[[this_name]] ,
                             docid_field = "eo_id", text_field = "speech")
  save_name <- paste0(this_name, "x.rds")
  write_rds(df, path = save_name)
}


# 
# lab_corpus_sample <- corpus(lab_speech_sample,
#                             docid_field = "eo_id", text_field = "speech")
# 
# system.time(
#   lab_annotate_sample <- spacy_parse(lab_corpus_sample, tag = TRUE,
#                                    dependency = TRUE,  lemma = FALSE,
#                                    pos = FALSE) # need to use lab_corpus for this
# )

## use a loop for this?
#devtools::install_github("quanteda/spacyr")
library(spacyr)
library(progress)
spacy_install(python_path = "/Users/evanodell/Documents/anaconda3/bin/python3")
spacy_initialize()

atemp <- list.files(pattern = "*x.rds")

pb <- progress_bar$new(total = length(atemp))

for (i in atemp) {
  
  lab_corpus <- read_rds(i)
  
  i <- gsub("x.rds", "", i)
  
   # need to use corpus object for this
  lab_annotate <- spacy_parse(lab_corpus, tag = TRUE, dependency = TRUE,
                            lemma = FALSE, pos = FALSE, entity = TRUE) 
 

  save_name <- paste0("ano_", i, ".rds")
  
  write_rds(lab_annotate, path = save_name)
  
  pb$tick()

}


write_rds(lab_annotate, "lab_annotate.rds")

```



## topic models

<!--
```{r topic-model-short-list, eval=FALSE, include=FALSE}

lab_corpus_fem_sl <- corpus_subset(lab_corpus, gender == "Female",
                                   short_list == TRUE)

lab_corpus_fem_dfm_sl <- dfm(lab_corpus_fem_sl, remove_punct = TRUE,
                          remove = parliament_stopwords) %>% 
  dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
           max_docfreq = 0.1, docfreq_type = "prop")

lab_corpus_fem_dfm_sl <- lab_corpus_fem_dfm_sl[ntoken(lab_corpus_fem_dfm_sl) > 0,]

dtm_sl <- convert(lab_corpus_fem_dfm_sl, to = "topicmodels")
fem_lda_sl <- LDA(dtm_sl, k = 15) #

docvars(lab_corpus_fem_dfm_sl, 'topic') <- topics(fem_lda_sl)

write_rds(fem_lda_sl, "fem_lda_sl.rds")

write_rds(lab_corpus_fem_dfm_sl, "lab_corpus_fem_dfm_sl.rds")
```

```{r topic-model-non-short-list, eval=FALSE, include=FALSE}

lab_corpus_fem_not_sl <- corpus_subset(lab_corpus, gender == "Female",
                                       short_list == FALSE)

lab_corpus_fem_dfm_not_sl <- dfm(lab_corpus_fem_not_sl, remove_punct = TRUE,
                             remove = parliament_stopwords) %>% 
  dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
           max_docfreq = 0.1, docfreq_type = "prop")

lab_corpus_fem_dfm_not_sl <- lab_corpus_fem_dfm_not_sl[ntoken(lab_corpus_fem_dfm_not_sl) > 0,]

dtm_not_sl <- convert(lab_corpus_fem_dfm_not_sl, to = "topicmodels")
fem_lda_not_sl <- LDA(dtm_not_sl, k = 15) #

docvars(lab_corpus_fem_dfm_not_sl, 'topic') <- topics(fem_lda_not_sl)

write_rds(fem_lda_not_sl, "fem_lda_not_sl.rds")

write_rds(lab_corpus_fem_dfm_not_sl, "lab_corpus_fem_dfm_not_sl.rds")

```
-->


<!--
## Career Advancement

Do AWS MPs advance more?

```{r}
library(readxl)
library(mnis)
library(dplyr)

all_women97_15 <- read_excel("list-of-mps.xlsx")

women_list <- lapply(all_women97_15$mnis, mnis_opposition_posts)

women_oppo <- bind_rows(women_list)

oppo <- janitor::clean_names(as.data.frame(t(mnis_base("holdsoppositionpost*TRUE"))))

govt <- janitor::clean_names(as.data.frame(t(mnis_base("holdsgovernmentpost*TRUE"))))

```


--->





<!--
```{r STM-classification-old, eval=FALSE, include=FALSE}
library(stm)
library(quanteda)
library(quanteda.corpora)
library(topicmodels)
library(readr)

lab_corpus <- read_rds("lab_corpus.rds")

lab_corpus_fem <- corpus_subset(lab_corpus, gender=="Female")

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister", "c")
rm(lab_corpus)
#ndoc(lab_corpus_fem)

lab_corpus_fem_dfm <- dfm(lab_corpus_fem, remove_punct = TRUE,
                           remove = parliament_stopwords, verbose = TRUE) #%>% 
#  dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
#           max_docfreq = 0.1, docfreq_type = "prop")

topic_model <- stm(lab_corpus_fem_dfm, K = 0, 
                   verbose = TRUE, init.type = "Spectral")

write_rds(topic_model, "stm-topic-model.rds")
```
-->



<!--
- 49 topic models
```{r STM-creation, eval=FALSE, include=FALSE}
library(stm)
library(quanteda)
library(quanteda.corpora)
library(topicmodels)
library(readr)

lab_corpus <- read_rds("lab_corpus.rds")

lab_corpus_fem <- corpus_subset(lab_corpus, gender=="Female")

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister", "c")
rm(lab_corpus)
#ndoc(lab_corpus_fem)

lab_corpus_fem_dfm <- dfm(lab_corpus_fem, remove_punct = TRUE,
                           remove = parliament_stopwords, verbose = TRUE) #%>% 
#  dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
#           max_docfreq = 0.1, docfreq_type = "prop")

topic_model_lda49 <- stm(lab_corpus_fem_dfm, K = 49, 
                         verbose = TRUE, init.type = "LDA")

write_rds(topic_model_lda49, "topic_model_lda49.rds")
```
-->
<!--
We assigned topic models using unsupervised Latent Dirichlet Allocation [@blei2003], implemented in the `topicmodels` R package [@grun2011]. See [TABLE NUMBER?] for the ten most common words in each topic model. Topic models were trained on all speeches by female Labour MPs.
```{r topic-model-women, eval=FALSE, include=FALSE}
library(quanteda)
library(quanteda.corpora)
library(topicmodels)
library(readr)

lab_corpus <- read_rds("lab_corpus.rds")

lab_corpus_fem <- corpus_subset(lab_corpus, gender=="Female")

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister", "c")
rm(lab_corpus)
#ndoc(lab_corpus_fem)

lab_corpus_fem_dfm <- dfm(lab_corpus_fem, remove_punct = TRUE,
                           remove = parliament_stopwords, verbose = TRUE) %>% 
  dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
           max_docfreq = 0.1, docfreq_type = "prop")

lab_corpus_fem_dfm <- lab_corpus_fem_dfm[ntoken(lab_corpus_fem_dfm) > 0,]

dtm <- convert(lab_corpus_fem_dfm, to = "topicmodels")
#fem_lda <- LDA(dtm, k = 20) #50 is too many, try again with 20
fem_lda <- LDA(dtm, k = 10)

### Analyse these

#terms(fem_lda, 10)

docvars(lab_corpus_fem_dfm, 'topic') <- topics(fem_lda)
#head(topics(fem_lda), 20)

write_rds(fem_lda, "fem_lda.rds")

docvars(lab_corpus_fem_dfm, "topic") <- topics(fem_lda)

write_rds(lab_corpus_fem_dfm, "lab_corpus_fem_dfm.rds")
```

```{r topic-model-analysis, eval=FALSE, message=FALSE, include=FALSE}
library(readr)
library(topicmodels)
library(quanteda)
library(dplyr)
library(ggplot2)
library(stringi)

fem_lda <- read_rds("fem_lda.rds")

#terms(fem_lda, 10)

lab_corpus_fem_dfm <- read_rds("lab_corpus_fem_dfm.rds")

terms_table <- tibble::as.tibble(terms(fem_lda, 20))

fem_df <- as.data.frame(docvars(lab_corpus_fem_dfm))

fem_df$topic <- as.factor(case_when(
  stri_length(fem_df$topic) == 1 ~ paste0("Topic 0", fem_df$topic),
  TRUE ~ paste0("Topic ", fem_df$topic)))

fem_df2 <- fem_df %>%
  group_by(short_list, topic) %>%
  summarise(topic_count = n()) %>%
    mutate(freq = topic_count / sum(topic_count)) 

fem_df2 <- fem_df2[order(-fem_df2$short_list, fem_df2$topic),]

# fem_df2$topic <- recode(fem_df2$topic,
#  "Topic 01" = "Children & Families",
#  "Topic 02" = "Education",
#  "Topic 03" = "Issues",
#  "Topic 04" = "Transport",
#  "Topic 05" = "Economy",
#  "Topic 06" = "Crime",
#  "Topic 07" = "Science",
#  "Topic 08" = "Health",
#  "Topic 09" = "Housing",
#  "Topic 10" = "Regions",
#  "Topic 11" = "Legal",
#  "Topic 12" = "Tax",
#  "Topic 13" = "Constituency",
#  "Topic 14" = "Debate",
#  "Topic 15" = "Process",
#  "Topic 16" = "Legal",
#  "Topic 17" = "Gender",
#  "Topic 18" = "Other",
#  "Topic 19" = "Legislation",
#  "Topic 20" = "Defence")
# 


# p_lda <- ggplot(fem_df2, aes(x = short_list, y=freq)) +
#   geom_col(aes(fill = topic)) +
#   scale_y_continuous(labels=scales::percent) +
#   labs(title = "Frequency of Topic Models",
#        subtitle = "Female Labour MPs grouped by selection process",
#        fill = "Topic Model") +
#   ylab("") +
#   xlab("Elected Through All Women Short list")
# 
# p_lda

p_lda2 <- ggplot(data = fem_df2, aes(y = freq, fill = short_list, x = topic)) + 
  geom_col(position = "dodge") + 
    scale_fill_manual(labels = c("Non-AWS", "AWS"),
                     values = c("#ff674c", "#02d5a1"), name = NULL) +
  scale_y_continuous(labels=scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  xlab("") + 
  ylab("Percentage of Speeches")

ggsave("p_lda2.eps", plot = p_lda2, path="plots", device = "eps")

p_lda2
```

```{r tidy-topic-model, eval=FALSE, include=FALSE}
library(tidytext)

beta_df <- tidy(fem_lda)

beta_df_gamma <- tidy(fem_lda, matrix = "gamma")
#beta_df_gamma

speech_classifications <- beta_df_gamma %>%
  group_by(document) %>%
  top_n(1, gamma) %>%
  ungroup() %>%
  arrange(gamma)

summary(speech_classifications)

speech_classifications2 <- beta_df_gamma %>%
  group_by(document) %>%
  top_n(2, gamma) %>%
  ungroup() %>%
  arrange(gamma) %>%
  group_by(document) %>%
  top_n(-1, gamma) %>%
  ungroup() %>%
  arrange(gamma)

summary(speech_classifications2)

# lab_speech <- read_rds("lab_speech.rds")
# 
# lda_texts <- left_join(speech_classifications, lab_speech,
#                        by = c("document"="eo_id"))

# x$diff <- x$gamma.y - x$gamma.x
# 
# summary(x$diff)
# 
# y <- filter(speech_classifications, document == "1028176")

```

```{r topic-model-table, eval=FALSE, include=FALSE}
library(pander)
pander(terms_table, caption = "Topic Model Terms",
       split.table = 80, style = 'rmarkdown', justify = 'left')

# library(knitr)
# library(kableExtra)
# kable(terms_table, caption = "Topic Model Terms")  %>%
#   kable_styling(full_width = TRUE, latex_options = "striped") %>%
#   landscape()

```

```{r topic-model-distribution-table, eval=FALSE, include=FALSE}
library(tidyr)
#fem_df2$freq <- paste0(round(fem_df2$freq * 100, 2), "%")

fem_df2 <- fem_df2 %>% ungroup() %>% select(-freq)

fem_df2_table <- fem_df2 %>% ungroup() %>%
  spread(short_list, topic_count) %>%
  mutate(not_sl_freq = (`FALSE` / sum(`FALSE`))*100, 
         sl_freq = (`TRUE` / sum(`TRUE`))*100) %>%
  rename("not_sl_total" = `FALSE`, "sl_total" = `TRUE`)

fem_df2_table$proportion <- fem_df2_table$sl_freq/fem_df2_table$not_sl_freq

library(knitr)
library(kableExtra)
kable(fem_df2_table, caption = "Topic Model Distribution", digits = 2, 
      col.names = c("Topic", "Not Short List Total", "Short List Total",
                    "Not Short List Percentage", "Short List Percentage",
                    "Relative Occurence")) %>%
  kable_styling(latex_options = "striped", full_width = FALSE)


```
-->




<!--
```{r svm, eval=FALSE, include=FALSE}
library(readr)
library(quanteda)
library(tidyr)
library(e1071) ## look up name of this SVM library
library(dplyr)

parliament_stopwords <- c(stopwords(), "hon", "rose", "n", "friend", "way", 
                          "give", "gentleman", "right", "percent", "per",
                          "cent", "prime", "minister")

lab_corpus <- read_rds("lab_corpus.rds")

lab_corpus2 <- corpus_sample(lab_corpus, size = ndoc(lab_corpus)/500, replace = TRUE)

lab_dfm2 <- lab_corpus2 %>% 
  dfm(remove = parliament_stopwords, remove_punct = TRUE,
      verbose = TRUE) 

lab_df <- as.matrix(lab_dfm2)

lab_df <- as.data.frame(lab_df, row.names = docnames(lab_dfm2))

# x2 <- convert(lab_dfm2, to = "tripletlist")
# 
# x <- slam::as.simple_triplet_matrix(lab_dfm2)
# 
# models <- svm(x=x2$vocab, y=x2$meta$gender)

lab_df$eo_id <- row.names(lab_df)

lab_docvars <- docvars(lab_corpus2)

lab_docvars$eo_id <- row.names(lab_docvars)

lab_docvars <- select(lab_docvars, gender, eo_id) %>% rename(mp_gender=gender)

lab_df <- left_join(lab_df, lab_docvars)

lab_df$mp_gender <- as.factor(lab_df$mp_gender)

row.names(lab_df) <- lab_df$eo_id

lab_df <- lab_df %>% select(mp_gender, everything(), -eo_id)

# #x <- x[,2:3402]
# 
# x2 <- as.data.frame(t(x))
# 
# x2 <- x2[,2:3402]
# 
# x3 <- gather(x2, key = "gender", value = "count")
# # 
# # x2 <- as.data.frame(t(x))
# # 
# # 

x <- colSums(lab_df[,!names(lab_df)=="mp_gender"])

summary(x)

index <- 1:nrow(lab_df)
   testindex <- sample(index, trunc(length(index)/3))
   testset   <- lab_df[testindex,]
   trainset  <- lab_df[-testindex,]

   
# library(sampling)
# strata_training <- strata(trainset, stratanames = "emptyvar", size = c(1000,500))
# #this creates a sample of size 1000 and 500 for 0 and 1 each
# strata.train<-getdata(train,Training)
# #it creates additional 3 columns which you can remove
# train<-strata.train[,!colnames(strata.train) %in% c("ID_unit","Prob","Stratum")]
#    
## Need to make sure that all columns have at least some values other than 0

model <- svm(mp_gender~., data = trainset) ## This is failing, find out why
pred  <- predict(model, testset[,-10])   



## need to get svm(x,y) working, with vector of document classes

lab_dfm_fem <- read_rds("lab_dfm_key_fem.rds")

vm.model <- svm(docs ~ ., data = x, cost = 100, gamma = 1)

 data(Glass, package="mlbench")
 ## split data into a train and test set
   index     <- 1:nrow(Glass)
   testindex <- sample(index, trunc(length(index)/3))
   testset   <- Glass[testindex,]
   trainset  <- Glass[-testindex,]

```
-->

<!--
```{r}
#"want me to make these points"

lab_speech <- read_rds("lab_speech.rds")

example1 <- lab_speech[grep("want me to make these points", lab_speech$speech),]

#"Ric Potter"

example2 <- lab_speech[grep("Ric Potter", lab_speech$speech),]

#"My constituents want more than pressure"
example3 <- lab_speech[grep("My constituents want more than pressure", lab_speech$speech),]


```
-->
